### 2016-11-09 elsarticle-template.tex
Initial ShareLaTeX Import

%%
%% Copyright 2007, 2008, 2009 Elsevier Ltd
%%
%% This file is part of the 'Elsarticle Bundle'.
%% ---------------------------------------------
%%
%% It may be distributed under the conditions of the LaTeX Project Public
%% License, either version 1.2 of this license or (at your option) any
%% later version.  The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.2 or later is part of all distributions of LaTeX
%% version 1999/12/01 or later.
%%
%% The list of all files belonging to the 'Elsarticle Bundle' is
%% given in the file `manifest.txt'.
%%

%% Template article for Elsevier's document class `elsarticle'
%% with numbered style bibliographic references
%% SP 2008/03/01
%%
%%
%%
%% $Id: elsarticle-template-num.tex 4 2009-10-24 08:22:58Z rishi $
%%
%%
\documentclass[preprint,12pt,3p]{elsarticle}

%% Use the option review to obtain double line spacing
%% \documentclass[preprint,review,12pt]{elsarticle}

%% Use the options 1p,twocolumn; 3p; 3p,twocolumn; 5p; or 5p,twocolumn
%% for a journal layout:
%% \documentclass[final,1p,times]{elsarticle}
%% \documentclass[final,1p,times,twocolumn]{elsarticle}
%% \documentclass[final,3p,times]{elsarticle}
%% \documentclass[final,3p,times,twocolumn]{elsarticle}
%% \documentclass[final,5p,times]{elsarticle}
%% \documentclass[final,5p,times,twocolumn]{elsarticle}

%% if you use PostScript figures in your article
%% use the graphics package for simple commands
%% \usepackage{graphics}
%% or use the graphicx package for more complicated commands
%% \usepackage{graphicx}
%% or use the epsfig package if you prefer to use the old commands
%% \usepackage{epsfig}

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
%% The amsthm package provides extended theorem environments
%% \usepackage{amsthm}

%% The lineno packages adds line numbers. Start line numbering with
%% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it on
%% for the whole article with \linenumbers after \end{frontmatter}.
%% \usepackage{lineno}

%% natbib.sty is loaded by default. However, natbib options can be
%% provided with \biboptions{...} command. Following options are
%% valid:

%%   round  -  round parentheses are used (default)
%%   square -  square brackets are used   [option]
%%   curly  -  curly braces are used      {option}
%%   angle  -  angle brackets are used    <option>
%%   semicolon  -  multiple citations separated by semi-colon
%%   colon  - same as semicolon, an earlier confusion
%%   comma  -  separated by comma
%%   numbers-  selects numerical citations
%%   super  -  numerical citations as superscripts
%%   sort   -  sorts multiple citations according to order in ref. list
%%   sort&compress   -  like sort, but also compresses numerical citations
%%   compress - compresses without sorting
%%
%% \biboptions{comma,round}

% \biboptions{}

\journal{STAT 241A}

\begin{document}

\begin{frontmatter}

\title{Mixing time of stochastic gradient descent}

\author{Yu Wang, 3031741324}
%\address[label2]{Address Two\fnref{label4}}

\begin{abstract}
Stochastic gradient descent (SGD), under mild conditions, can be viewed as a Markov chain, which is called Ornstein-Uhlenbeck process. This relationship has been pointed out in a variety of papers. Although SGD has been extensively studied, its property as a Markov chain seems to be largely overlooked. An interesting problem is its mixing time, i.e., how fast the markov chain will converge to the stationary distribution. This is well related to many topics, including variational Bayesian analysis \cite{??}, ..., and etc..

Although the problem is interesting, there aren't a lot of schemes availabel to analyzing SGD's mixing time. Traditional ways includs ..... A course book...(Do some survey) However, these methods might not be able to be applied to SGD in a direct way.

My proposal is to try to bridge the gap between classical mixing time analysis and SGD and obtain some novel lower/upper bounds on the mixing time of SGD (If successful). Simulations will be carried out to understand how good my estimates are as well as the estimates in other literature.

Once the mixing time of SGD has been bounded. The second part will dedicated to study the relationship between mixing time and convergence rate. The intuition is that if the corresponding MCMC have a low mixing time, SGD should converge fast. This seems to be a novel perspective to understand SGD. Theoretical analysis as well as empirical experiments will be carried out to further explore this issue. 
\end{abstract}

\begin{keyword}
%% keywords here, in the form: keyword \sep keyword
example \sep \LaTeX \sep template
%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\end{keyword}

\end{frontmatter}

%%
%% Start line numbering here if you want
%%
% \linenumbers

%% main text
\section{Sample section}
\label{sec1}

Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
Sample text. Sample text. Citation of Einstein paper~\cite{Einstein}.

\subsection{Sample subsection}
\label{subsec1}

Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
Sample text.

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

\section{Section in Appendix}
\label{appendix-sec1}

Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
Sample text. Sample text. Sample text. Sample text. Sample text. Sample text. 
Sample text.

%% References
%%
%% Following citation commands can be used in the body text:
%% Usage of \cite is as follows:
%%   \cite{key}         ==>>  [#]
%%   \cite[chap. 2]{key} ==>> [#, chap. 2]
%%

%% References with bibTeX database:

\bibliographystyle{elsarticle-num}
% \bibliographystyle{elsarticle-harv}
% \bibliographystyle{elsarticle-num-names}
% \bibliographystyle{model1a-num-names}
% \bibliographystyle{model1b-num-names}
% \bibliographystyle{model1c-num-names}
% \bibliographystyle{model1-num-names}
% \bibliographystyle{model2-names}
% \bibliographystyle{model3a-num-names}
% \bibliographystyle{model3-num-names}
% \bibliographystyle{model4-names}
% \bibliographystyle{model5-names}
% \bibliographystyle{model6-num-names}

\bibliography{sample}

\end{document}

%%
%% End of file `elsarticle-template-num.tex'.

### 2016-11-09 main.tex
Updates from ShareLaTeX

--- 2016-11-09 elsarticle-template.tex
@@
 \begin{abstract}
-Stochastic gradient descent (SGD), under mild conditions, can be viewed as a Markov chain, which is called Ornstein-Uhlenbeck process.
-This relationship has been pointed out in a variety of papers.
-Although SGD has been extensively studied, its property as a Markov chain seems to be largely overlooked.
-An interesting problem is its mixing time, i.e., how fast the markov chain will converge to the stationary distribution.
-This is well related to many topics, including variational Bayesian analysis \cite{??}, ..., and etc..
 
-Although the problem is interesting, there aren't a lot of schemes availabel to analyzing SGD's mixing time.
-Traditional ways includs .....
-A course book...(Do some survey) However, these methods might not be able to be applied to SGD in a direct way.
-
-My proposal is to try to bridge the gap between classical mixing time analysis and SGD and obtain some novel lower/upper bounds on the mixing time of SGD (If successful).
-Simulations will be carried out to understand how good my estimates are as well as the estimates in other literature.
-
-Once the mixing time of SGD has been bounded.
-The second part will dedicated to study the relationship between mixing time and convergence rate.
-The intuition is that if the corresponding MCMC have a low mixing time, SGD should converge fast.
-This seems to be a novel perspective to understand SGD.
-Theoretical analysis as well as empirical experiments will be carried out to further explore this issue.
 \end{abstract}

### 2016-11-13 main.tex
type and related work

--- 2016-11-09 elsarticle-template.tex
@@
 
-\author{Yu Wang, 3031741324}
+\author{Yu Wang, 3031741324\\ Weixin Cai, 26954913}
 %\address[label2]{Address Two\fnref{label4}}
@@
 
-Although the problem is interesting, there aren't a lot of schemes availabel to analyzing SGD's mixing time.
-Traditional ways includs .....
-A course book...(Do some survey) However, these methods might not be able to be applied to SGD in a direct way.
+Although the problem is interesting, there aren't a lot of schemes available to analyzing SGD's mixing time.
+Traditional ways includes .....
+A course book...(Do some survey).
+However, these methods might not be able to be applied to SGD in a direct way.
 
@@
 This seems to be a novel perspective to understand SGD.
+Duchi et al.\cite{duchi2012ergodic} shows how the finite-sample convergence rate (expected convergence \& high-probability convergence) of stochastic sub-gradient descent depends on the mixing time of the process.
+If we can bound the mixing time, subsequently, we will be able to understand the convergence of this class of optimization techniques.
 Theoretical analysis as well as empirical experiments will be carried out to further explore this issue.

### 2016-11-15 main.tex
background book
complete the abstract.

--- 2016-11-09 main.tex
@@
 \begin{abstract}
+Stochastic gradient descent (SGD), under mild conditions, can be viewed as a Markov chain.
+This relationship has been pointed out in a variety of papers \cite{kushner2012stochastic, bach2014adaptivity}.
+Although SGD has been extensively studied, its property as a Markov chain seems to be largely overlooked.
+What is its stationary distribution?
+What is its mixing time?
+How does its mixing time relate to its convergence rate?
+Studying these properties could offer a novel perspective to understand SGD.
 
+Currently, there aren't a lot of schemes available to analyzing SGD's mixing time.
+Traditional ways includes coupling, diameter bounds, and bottle-neck ratio etc.
+(see \emph{Reversible Markov chains and random walks on graphs} by Aldous et al.\cite{aldous2002reversible}, and \emph{Markov chains and mixing times} by Levin et al.\cite{levin2009markov}).
+However, these methods are designed for the Markov chain on a graph and might not be able to be applied to SGD directly.
+
+Our proposal is to bridge the gap between classical Markov chain analysis and SGD.
+Specifically,  we would like to explore mixing time related issues and obtain some novel theoretical and empirical findings on the mixing time of SGD (If successful).
+A specific question to answer is whether lower mixing time will imply faster convergence rate.
+The hunch is that if the corresponding Markov chain has a low mixing time, SGD should converge fast.
+This seems to be a novel perspective to understand SGD.
+Duchi et al.\cite{duchi2012ergodic} shows how the finite-sample convergence rate (expected convergence \& high-probability convergence) of stochastic sub-gradient descent depends on the mixing time of the process.
+If we can bound the mixing time, subsequently, we will be able to understand the convergence of this class of optimization techniques.
+Theoretical analysis as well as empirical experiments will be carried out to further explore this issue.
+
+Our group contains two people. The tentative plan is that Yu focuses on the theoretical exploration and Weixin focuses on the empirical experiments. The final report will be written together.
 \end{abstract}

### 2016-11-15 code/proof_of_concept.py
script version of same code as ipynb

@@ -1,0 +1,144 @@
+#Gradient Descent
+import numpy as np
+import matplotlib.pyplot as plt
+import random
+# ========================================================================================
+# SGD
+# ========================================================================================
+def GD(objective, gradient, initialPoint, stepsize, noiseLevel, maxIter, desiredObj,
+       seed = None,
+       verbose = True):
+    '''
+    Perform stochastic gradient descent to maximize objective.
+
+    Args:
+    objective    - function handle, return objective
+    gradient     - function handle, return gradient
+    initialPoint - array of dimension d, starting point
+    stepsize     - numeric,
+    noiseLevel   - numeric, the variance of the Gaussian noise
+    maxIter      - integer, the iterations
+    desiredObj   - double, the desired objective function value (algorithm halts when it is reached)
+    verbose      - boolean, whether to print intermediate results
+
+    Returns:
+    trajectory   - 2d array of maxIter * d, the record of x
+    image        - 2d array of maxIter * 1, the record of objective
+    haltIter     - integer, the stopped iteration
+    '''
+    # initial config
+    if isinstance(initialPoint, float):
+        d = 1
+    else:
+        d = len(initialPoint)
+    rng = random.Random()
+    if seed is not None:
+        rng.seed(seed)
+
+    trajectory = np.zeros((maxIter, d))
+    image      = np.zeros((maxIter, 1))
+    x          = initialPoint
+    trajectory[0] = x
+    image[0]      = objective(x)
+
+    for iter in range(1, maxIter):
+        # SGD step
+        # add noise to the true gradient
+        noise = rng.normalvariate(0, noiseLevel)
+        # WILSON?: stepsize * (gradient(x) + noise)
+        x = x + stepsize * gradient(x) + noise
+        trajectory[iter] = x
+        image[iter] = objective(x)
+        if image[iter] > desiredObj:
+            if verbose:
+                print('Reached desired Objective at step %d' % iter)
+            break
+    if verbose and image[iter] < desiredObj:
+        print('Did not converge while max iteration reached %d' % iter)
+    haltIter = iter
+    return trajectory, image, haltIter
+
+# ========================================================================================
[…]

### 2016-11-20 code/convergence.py
mixing time

@@ -1,0 +1,22 @@
+def convergence_time(one_trajectory, modes, epsilon_neighbor = 1e-2):
+    n_mode = len(modes)
+    converge_t_by_mode = []
+
+    for it in range(0,n_mode):
+        time_reach = np.where(abs(np.array(one_trajectory) - modes[it]) < epsilon_neighbor)[0]
+        if len(time_reach) == 0:
+            # indicate not converge to the mode with -1
+            time_here = -1
+        else:
+            time_here = time_reach[0]
+        converge_t_by_mode.append(time_here)
+
+    if all(np.array(converge_t_by_mode) > 0):
+        # if converge to all modes,
+        # we return the convergence time as the time trajectory reaches all modes
+        return max(converge_t_by_mode)
+    else:
+        # if not converge, return -1
+        return -1
+
+# convergence_time(one_trajectory = one_trajectory, modes = [100], epsilon_neighbor=1e-2)

### 2016-11-20 code/mixing.py

@@ -1,0 +1,50 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
+
+def graph(formula, x_range = range(-3, 3)):
+    '''
+    graph any function within a range
+    '''
+    # x = np.array(x_range)
+    x = np.linspace(start = x_range[0], stop = x_range[len(x_range)-1], num=50, endpoint=True)
+    y = formula(x)  # <- note now we're calling the function 'formula' with x
+    plt.plot(x, y)
+    plt.show()
+# ====================================================================================
+def pdf_to_cdf(pdf_func, a = -3, b = 3, dx = .01):
+    # WILSON: from -inf to a: the mass is missing
+    X  = np.arange(a,b,dx)
+    Y  = pdf_func(X)
+    Y /= (dx*Y).sum()
+    CY = np.cumsum(Y*dx)
+    step = sm.distributions.empirical_distribution.StepFunction(x = X, y = CY,side='left')
+    return step
+
+def cdf_l1(cdf1, cdf2, a=-3, b=3, dx=.01):
+    X  = np.arange(a,b,dx)
+    val1 = cdf1(X)
+    val2 = cdf2(X)
+    return np.mean(abs(val1 - val2))
+# ====================================================================================
+# plt.figure()
+# graph(ecdf, range(-3, 3))
+# graph(station_cdf, range(-3, 3))
+
+def is_mix(emp_samples, station_func, epsilon_norm = 1e-2, a=-3, b=3, dx=.01):
+    ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    station_cdf = pdf_to_cdf(pdf_func = station_func, a=a, b=b, dx=dx)
+
+    l1_norm = cdf_l1(cdf1 = ecdf, cdf2 = station_cdf, a=a, b=b, dx=dx)
+    if l1_norm <= epsilon_norm:
+        return True
+    else:
+        return False
+# ====================================================================================
+
+def mixing_time(all_trajectory, station_func, epsilon_norm = 1e-2):
+    pass
+
+

### 2016-11-20 code/proof_of_concept.py
sgd module

@@ -82,7 +82,7 @@ def ProofOfConcept():
     x = np.arange(-2, 2, 1e-3)
     plt.plot(x, np.exp(func(x)))
 
-ProofOfConcept()
+# ProofOfConcept()
 
 
 
@@ -109,10 +109,10 @@ def ProofOfConcept2():
     x = np.arange(-3, 3, 1e-3)
     plt.plot(x, np.exp(func(x)))
 
-ProofOfConcept2()
+# ProofOfConcept2()
 
-x = np.arange(-.6, .6, 1e-3)
-plt.plot(x, np.exp(-100*x**4))
+# x = np.arange(-.6, .6, 1e-3)
+# plt.plot(x, np.exp(-100*x**4))
 
 
 # ========================================================================================
@@ -137,8 +137,8 @@ def GD_UnitTest(order = 1):
     # values are trajectory
     plt.hist(trajectory[haltIter/2:haltIter], 100)
 
-GD_UnitTest(order = 1)
-plt.interactive(True)
+# GD_UnitTest(order = 1)
+# plt.interactive(True)
 
-yp = trajectory[haltIter/2:haltIter]
-len(yp)
+# yp = trajectory[haltIter/2:haltIter]
+# len(yp)

### 2016-11-20 code/convergence.py
convergence and mixing time module complete

@@ -1,3 +1,8 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
 def convergence_time(one_trajectory, modes, epsilon_neighbor = 1e-2):
     n_mode = len(modes)
     converge_t_by_mode = []
@@ -20,3 +25,9 @@ def convergence_time(one_trajectory, modes, epsilon_neighbor = 1e-2):
         return -1
 
 # convergence_time(one_trajectory = one_trajectory, modes = [100], epsilon_neighbor=1e-2)
+def convergence_time_all(all_trajectory, modes, epsilon_neighbor = 1e-2):
+    n_total = all_trajectory.shape[1]
+    time_all = np.empty(shape = n_total)
+    for it in range(0,n_total):
+        time_all[it] = convergence_time(one_trajectory = all_trajectory[:,it], modes = modes, epsilon_neighbor=epsilon_neighbor)
+    return time_all

### 2016-11-20 code/mixing.py

@@ -43,8 +43,14 @@ def is_mix(emp_samples, station_func, epsilon_norm = 1e-2, a=-3, b=3, dx=.01):
     else:
         return False
 # ====================================================================================
-
-def mixing_time(all_trajectory, station_func, epsilon_norm = 1e-2):
-    pass
-
+def mixing_time(all_trajectory, station_func, epsilon_norm = 1e-1, a=-3, b=3, dx=.01):
+    N_total = all_trajectory.shape[0]
+    is_mix_all = np.empty(shape = N_total, dtype = 'bool')
+    for it in range(0,N_total):
+        is_mix_all[it] = is_mix(all_trajectory[it,:], station_func = station_func, epsilon_norm=epsilon_norm, a=a, b=b, dx=dx)
+    mix_index = np.where(is_mix_all)[0]
+    if len(mix_index) == 0:
+        return -1
+    else:
+        return mix_index[0]
 

### 2016-11-20 code/simulation.py
simulation module

@@ -1,0 +1,68 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
+import ipyparallel
+
+def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, verbose = False):
+    trajectory_all = []
+    image_all = []
+    haltIter_all = []
+    for it in range(0,n_sim):
+        print(it)
+        trajectory, image, haltIter = sgd_base.GD(func, grad, initialPoint=initialPoint, stepsize=stepsize,
+                                 noiseLevel=noiseLevel, maxIter=maxIter, desiredObj=desiredObj, verbose = verbose)
+        trajectory_all.append(trajectory)
+        image_all.append(image)
+        haltIter_all.append(haltIter)
+    return trajectory_all, image_all, haltIter_all
+
+
+# $ ipcluster start -n 3
+
+
+def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100):
+    clients = ipyparallel.Client()
+    dview = clients.direct_view()
+
+    # # sync_imports does not support
+    # # import foo as bar
+    # # therefore need rewrite module names
+    # with dview.sync_imports():
+    #     import numpy as np
+    #     import matplotlib.pyplot as plt
+    #     import random
+    #     import proof_of_concept as sgd_base
+    #     import mixing as mixing
+    #     import convergence as convergence
+
+    # parallel cannot use lambda function either
+
+    dview.execute('import numpy as np')
+    dview.execute('import matplotlib.pyplot as plt')
+    dview.execute('import random')
+    dview.execute('import proof_of_concept as sgd_base')
+    dview.execute('import mixing as mixing')
+    dview.execute('import convergence as convergence')
+
+    dview.push(dict(func = func, grad = grad))
+
+    n_core = len(clients.ids)
+    n_sim_each = int(np.floor(n_sim/n_core))
+    # def helper(n_sim):
+        # return simu_all(n_sim=n_sim, func=func, grad=grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100, verbose=False)
+
[…]

### 2016-11-20 code/example1.py
example distribution 1

@@ -1,0 +1,45 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
+
+plt.interactive(True)
+
+import ipyparallel
+
+import proof_of_concept as sgd_base
+import mixing
+import convergence
+import simulation
+# %run mixing
+# %run convergence
+%run simulation
+
+
+# EG1: f(x) = -x**4
+degree = 4
+maxIter = int(1e5)
+def func(x, degree = degree):
+    return -np.power(x, degree)
+def grad(x, degree = degree):
+    return -degree * np.power(x, degree - 1)
+def station_func(x):
+    return np.exp(func(x))
+modes = [0]
+
+# trajectory, image, haltIter = sgd_base.GD(func, grad, initialPoint=1., stepsize=1e-2/2,
+#                                  noiseLevel=1e-1, maxIter=maxIter, desiredObj=100)
+# plt.hist(trajectory[haltIter/2:haltIter], 100)
+# ha = trajectory[haltIter/2:haltIter]
+
+# all_simu = simulation.simu_all_parallel(n_sim = 1e1, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
+all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
+
+mix_time = mixing.mixing_time(all_trajectory = all_traject, station_func = station_func, epsilon_norm=1e-1, a=-3, b=3, dx=.01)
+
+conv_time_all = convergence.convergence_time_all(all_trajectory = all_traject, modes = modes, epsilon_neighbor=1e-2)
+
+
+np.median(conv_time_all)
+mix_time

### 2016-11-20 code/example1.py
eg 1

@@ -19,7 +19,6 @@ import simulation
 
 # EG1: f(x) = -x**4
 degree = 4
-maxIter = int(1e5)
 def func(x, degree = degree):
     return -np.power(x, degree)
 def grad(x, degree = degree):
@@ -34,12 +33,15 @@ modes = [0]
 # ha = trajectory[haltIter/2:haltIter]
 
 # all_simu = simulation.simu_all_parallel(n_sim = 1e1, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
-all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
+all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad,
+                                initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1,
+                                 maxIter=int(1e5), desiredObj=100)
+# 100 n_sim = 1.25 min
 
-mix_time = mixing.mixing_time(all_trajectory = all_traject, station_func = station_func, epsilon_norm=1e-1, a=-3, b=3, dx=.01)
-
-conv_time_all = convergence.convergence_time_all(all_trajectory = all_traject, modes = modes, epsilon_neighbor=1e-2)
-
+mix_time = mixing.mixing_time(all_trajectory = all_traject, station_func = station_func,
+                                 epsilon_norm=1e-1, a=-3, b=3, dx=.01)
+conv_time_all = convergence.convergence_time_all(all_trajectory = all_traject,
+                                                 modes = modes, epsilon_neighbor=1e-2)
 
 np.median(conv_time_all)
 mix_time

### 2016-11-20 code/simulation.py
complete simu module

@@ -20,8 +20,6 @@ def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-
 
 
 # $ ipcluster start -n 3
-
-
 def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100):
     clients = ipyparallel.Client()
     dview = clients.direct_view()
@@ -50,11 +48,7 @@ def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noise
 
     n_core = len(clients.ids)
     n_sim_each = int(np.floor(n_sim/n_core))
-    # def helper(n_sim):
-        # return simu_all(n_sim=n_sim, func=func, grad=grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100, verbose=False)
 
-    # results = dview.map_sync(simu_all, [n_sim_each]*4)
-    # results = dview.map_sync(helper, [n_sim_each]*4, [func]*4, [grad]*4)
     results = dview.map_sync(simu_all, [n_sim_each]*n_core, [func]*n_core, [grad]*n_core)
 
     all_traject = np.empty(shape = maxIter)

### 2016-11-20 code/example2.py
example 2

@@ -1,0 +1,50 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
+
+plt.interactive(True)
+
+import ipyparallel
+
+import proof_of_concept as sgd_base
+import mixing
+import convergence
+import simulation
+# %run mixing
+# %run convergence
+%run simulation
+
+
+# EG2: f(x) = -(x ** 2 - 4)*(x ** 2 - 1) * c
+# \hat f(x) == exp(c*f(x))
+c = 1
+def func(x, c = c):
+    return -(x ** 2 - 4)*(x ** 2 - 1) * c
+def grad(x, c = c):
+    return (-4 * x ** 3 + 10 * x) * c
+def station_func(x):
+    return np.exp(func(x))
+# mixing.graph(formula = func, x_range=range(-3, 5))
+modes = [-np.sqrt(2.5), np.sqrt(2.5)]
+
+
+# trajectory, image, haltIter = sgd_base.GD(func, grad, initialPoint=1., stepsize=1e-2/2,
+#                                  noiseLevel=1e-1, maxIter=maxIter, desiredObj=100)
+# plt.hist(trajectory[haltIter/2:haltIter], 100)
+# ha = trajectory[haltIter/2:haltIter]
+
+# all_simu = simulation.simu_all_parallel(n_sim = 1e1, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
+all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad,
+                                initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1,
+                                 maxIter=int(1e5), desiredObj=100)
+# 100 n_sim = 1.25 min
+
+mix_time = mixing.mixing_time(all_trajectory = all_traject, station_func = station_func,
+                                 epsilon_norm=1e-1, a=-3, b=3, dx=.01)
+conv_time_all = convergence.convergence_time_all(all_trajectory = all_traject,
+                                                 modes = modes, epsilon_neighbor=1e-2)
+
+np.median(conv_time_all)
+mix_time

### 2016-11-20 code/example1.py
add warning when not converge

@@ -43,5 +43,12 @@ mix_time = mixing.mixing_time(all_trajectory = all_traject, station_func = stati
 conv_time_all = convergence.convergence_time_all(all_trajectory = all_traject,
                                                  modes = modes, epsilon_neighbor=1e-2)
 
+# raise warnings when not converge;
+# we thus need to increase 'maxIter'
+import warnings
+if any(conv_time_all < 0):
+    warnings.warn(str(sum(conv_time_all < 0)) + ' out of ' + str(len(conv_time_all)) + ' did not converge! The covergence time is smaller than actual!')
+conv_time_all = np.delete(conv_time_all, np.where(conv_time_all < 0))
+
 np.median(conv_time_all)
 mix_time

### 2016-11-20 code/example2.py

@@ -46,5 +46,12 @@ mix_time = mixing.mixing_time(all_trajectory = all_traject, station_func = stati
 conv_time_all = convergence.convergence_time_all(all_trajectory = all_traject,
                                                  modes = modes, epsilon_neighbor=1e-2)
 
+# raise warnings when not converge;
+# we thus need to increase 'maxIter'
+import warnings
+if any(conv_time_all < 0):
+    warnings.warn(str(sum(conv_time_all < 0)) + ' out of ' + str(len(conv_time_all)) + ' did not converge! The covergence time is smaller than actual!')
+conv_time_all = np.delete(conv_time_all, np.where(conv_time_all < 0))
+
 np.median(conv_time_all)
 mix_time

### 2016-12-02 paper/main.tex
organize paper folder

--- 2016-11-15 main.tex
@@
 
-%% The amssymb package provides various useful mathematical symbols
 \usepackage{amssymb}
-%% The amsthm package provides extended theorem environments
-%% \usepackage{amsthm}
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{mathrsfs}
+\usepackage{algorithm}
+\usepackage{algorithmic}
 
@@
 % \biboptions{}
+\newcommand{\bx}{\mathbf{x}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\D}{\mathscr{D}}
+\newcommand{\N}{\mathscr{N}}
+\newcommand{\by}{\mathbf{y}}
+
+\newtheorem{conjecture}{Conjecture}
 
@@
 
-\title{Mixing time of stochastic gradient descent}
+\title{A Novel Sampling Method Using Stochastic Gradient Descent}
 
@@
 %% keywords here, in the form: keyword \sep keyword
-example \sep \LaTeX \sep template
+Stochastic gradient descent \sep Sampling \sep Metropolis-Hastings
 %% MSC codes here, in the form: \MSC code \sep code
@@
 %% main text
+\section{Main Theorems}
+
+\begin{algorithm}
+{\small
+Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$, 
+\begin{algorithmic}\caption{Stochastic gradient descent}\label{Alg:SGD}
+\STATE {\bf Initialize} $ \bx^0$ arbitrarily;
+\WHILE{stopping criterion not satisfied}
+\STATE draw $\epsilon^t$ from Gaussian distribution $\N(0, \sigma^2)$.
+\STATE
+$\bx^{k+1} \gets \bx^k - \alpha(\nabla f(\bx^k) + \epsilon^t)$;
+\STATE $k\gets k+1$;
+\ENDWHILE
+\STATE return $\bx^k$.
+\end{algorithmic}}
+\end{algorithm}
+
+Define $\D(\R^p)$ to be the family of the density functions of smooth random variables in $\R^p$, i.e.,
+
+\begin{equation}
+\D(\R^p)\triangleq \{p(\bx)\Big| p\in C^1(\R^p),~p(\bx) \geq 0,~ \int_\bx p(\bx) = 1.\}
+\end{equation}
+Consider any $p(\bx)\in \D(\R^p)$, we have the following theorem:
+
+\begin{conjecture}
+For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, \epsilon)$. 
+\end{conjecture}
+\begin{proof}
+Let's verify this theorem by checking the detailed balance condition.
+Denote $g(\by|\bx)$ to be the density function of the transition, because $\by = \bx - \alpha \nabla f(\bx^k) + \epsilon^t$ and $\epsilon^t\sim \N(0, \sigma^2)$, we know
+\begin{equation}
+g(\by|\bx) = (2\pi \sigma^2)^{-p/2} \exp(- \frac{\|\by - \bx + \alpha \nabla h(\bx)\|^2}{2\sigma^2}).
+\end{equation}
+Then the detailed balance condition is 
+\begin{equation}\label{Eq:detailBalance}
+p(\bx^{k+1}) g(\bx^{k}|\bx^{k+1}) = p(\bx^{k}) g(\bx^{k+1}|\bx^{k}).
+\end{equation}
+Since we will only consider $\bx^k$ and $\bx^{k+1}$ in the proof. For notation ease, we denote $\bx^{k+1}$ as $\bx^+$. 
+In order to prove \ref{Eq:detailBalance}, we would like to show the ratio between LHS and RHS to be 1. To be more specific, we have (Recall that $\sigma^2 = \alpha$)
+\begin{eqnarray}
+\frac{p(\bx^{+}) g(\bx^{k}|\bx^{+})}{p(\bx^{k}) g(\bx^{+}|\bx^{k})} = & \exp(-h(\bx^{+}) - \frac{\|\bx^{k} - \bx^+ + \alpha \nabla h(\bx^{+})\|^2}{2\alpha} + h(\bx^{k}) + \frac{\|\bx^{+} - \bx^k + \alpha \nabla h(\bx^k)\|^2}{2\alpha}).
+\end{eqnarray}
+Note that 
+\[h(\bx^+) - h(\bx^k) = \frac{\nabla h(\bx^k) + \nabla h(\bx^+)}{2} \cdot (\bx^+ - \bx^k) + O(\|\bx^+ - \bx^k\|^2),
+\]
+and 
+\begin{eqnarray}
+ & \frac{\|\bx^{k} - \bx^+ + \alpha \nabla h(\bx^{+})\|^2}{2\alpha} - \frac{\|\bx^{+} - \bx^k + \alpha \nabla h(\bx^k)\|^2}{2\alpha} \\
+ =& -\frac{\nabla h(\bx^k) + \nabla h(\bx^+)}{2} \cdot (\bx^+ - \bx^k) + \alpha/2 \|\nabla h(\bx^+)\|^2 - \alpha/2 \|\nabla h(\bx^+)\|^2.
+\end{eqnarray}
+Here, $\|\bx^+ - \bx^k\|$ will be roughly no bigger than $\alpha$ because $\bx^+ = \bx^k - \alpha \nabla h(\bx^k) + \epsilon^k$.
+Thus it means $O(\|\bx^+ - \bx^k\|) = O(\alpha^2)$.
+What's more, $\alpha/2 \|\nabla h(\bx^+)\|^2 - \alpha/2 \|\nabla h(\bx^+)\|^2 = O(\alpha^2)$.
+Thus we know 
+\begin{eqnarray}
+\log \frac{p(\bx^{+}) g(\bx^{k}|\bx^{+})}{p(\bx^{k}) g(\bx^{+}|\bx^{k})} = &O(\alpha^2).
+\end{eqnarray}
+Therefore, we know the detailed balance equality holds approximately especially when $\alpha$ is small.
+
+When $h$ is a quadratic function, this equation holds exactly. 
+\end{proof}
+
+Since this is only a very rough deduction, we would like to examine the stationary distribution of SGD empirically for some special cases.
+
+Some figures...
+
 \section{Sample section}
@@
 Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Citation of Einstein paper~\cite{Einstein}.
-
 \subsection{Sample subsection}

### 2016-12-02 code/mixing.py
clean

@@ -4,8 +4,6 @@ import random
 import scipy as sp
 import statsmodels as sm
 
-
-
 def graph(formula, x_range = range(-3, 3)):
     '''graph any function within a range
 

### 2016-12-04 paper/main.tex

@@
 \newtheorem{conjecture}{Conjecture}
+\newtheorem{theorem}{Theorem}
+\newtheorem{experiment}{Experiment}
 
@@
 \begin{conjecture}
-For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, \epsilon)$. 
+For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, 2\epsilon)$. 
 \end{conjecture}
@@
 
-When $h$ is a quadratic function, this equation holds exactly. 
+When $h$ is a quadratic function, the detailed balance holds exactly. 
 \end{proof}
+
+Some empirical demonstration. How accurate is this approximation?
 
@@
 
+\begin{experiment}
+Take the density function of $X$ to be $f(x) \propto \exp(- x^4)$, let $2\sigma^2 = \epsilon = 0.005$, $x_0 = 1$, burning-in period is $1000$, waiting period is $1000$, the empirical histogram v.s.
+the desired histogram is plotted in Figure ???
+\end{experiment}
+\begin{figure}
+    \centering
+    \includegraphics{figure/case1_step_0.005_iter_1e3.png}
+    \caption{Experiment 1: the empirical distribution using SGD}
+    \label{Fig:exp1}
+\end{figure}
+
+\section{Sampling from posterior distribution}
+Consider an statistical model fitting problem.
+Given data $X_1,\ldots, X_n$, we are fitting a model $P(X_i|\theta)$.
+The maximum likelihood estimate will be $\hat{\theta} \in \argmin - \sum_{i=1}^n \log P(X_i|\theta)$.
+This can be solved by gradient descent on objective function $- \sum_{i=1}^n \log P(X_i|\theta)$.
+Now let's consider a Bayesian approach to estimate $\theta$ by maximizing its posterior probability given the data.
+The posterior distribution of $\theta$ is
+$P(\theta|(X_1,\ldots, X_n)) = \frac{\prod_{i=1}^n P(X_i|\theta) P(\theta)}{P(X_1,\ldots, X_n)} \propto \prod_{i=1}^n P(X_i|\theta) P(\theta)$.
+Then we could use SGD to draw sample from it.
+Note that we could approximate the noisy gradient step by subsampling.
+By central limit theorem, we know it still holds.
+
+\begin{theorem}[Central limit theorem]
+
+\end{theorem}
+
+Suppose we would like to draw sample from a posterior distribution 
 Some figures...

### 2016-12-04 paper/main.tex
paper structure
add package for plotting
Updates from ShareLaTeX

@@
 \usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{grffile}
 
@@
 \newcommand{\by}{\mathbf{y}}
+\DeclareMathOperator*{\argmin}{\arg\!\min}
 
@@
 % \linenumbers
+% ===================================================================================
+\section{Introduction} % (fold)
+\label{sec:introduction}
 
+% section introduction (end)
+
+% ===================================================================================
 %% main text
@@
     \centering
-    \includegraphics{figure/case1_step_0.005_iter_1e3.png}
-    \caption{Experiment 1: the empirical distribution using SGD}
+    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e5.png}
+    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e5.png}
+    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e5.png}
+    \caption{Experiment 1: the empirical histogram using SGD.
+Each column corresponds to a different number of samples ($1e3$, $1e4$, and $1e5$), each row corresponds to a different distrubtion ($f_1(x) = \exp(-x^4)$, $f_3(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$}
     \label{Fig:exp1}
@@
 \section{Sampling from posterior distribution}
-Consider an statistical model fitting problem.
-Given data $X_1,\ldots, X_n$, we are fitting a model $P(X_i|\theta)$.
-The maximum likelihood estimate will be $\hat{\theta} \in \argmin - \sum_{i=1}^n \log P(X_i|\theta)$.
+Consider a statistical model fitting problem. Given $n$ samples $X_1,\ldots, X_n$ and an assumed model $P(X_1|\theta)$. The maximum likelihood estimate will be 
+\[
+\hat{\theta} \in \argmin - \sum_{i=1}^n \log P(X_i|\theta).
+\]
 This can be solved by gradient descent on objective function $- \sum_{i=1}^n \log P(X_i|\theta)$.
@@
 The posterior distribution of $\theta$ is
-$P(\theta|(X_1,\ldots, X_n)) = \frac{\prod_{i=1}^n P(X_i|\theta) P(\theta)}{P(X_1,\ldots, X_n)} \propto \prod_{i=1}^n P(X_i|\theta) P(\theta)$.
-Then we could use SGD to draw sample from it.
-Note that we could approximate the noisy gradient step by subsampling.
-By central limit theorem, we know it still holds.
+\[
+P(\theta|(X_1,\ldots, X_n)) = \frac{\prod_{i=1}^n P(X_i|\theta) P(\theta)}{P(X_1,\ldots, X_n)} \propto \prod_{i=1}^n P(X_i|\theta) P(\theta).
+\]
+Then we could use SGD to draw sample from it. Note that we could approximate the noisy gradient step by subsampling. By central limit theorem, we know it still holds.
 
@@
 
-\section{Sample section}
-\label{sec1}
+% ===================================================================================
+\section{Numerical experiments} % (fold)
+\label{sec:numerical_experiments}
 
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-\subsection{Sample subsection}
-\label{subsec1}
+% section numerical_experiments (end)
+% ===================================================================================
+\section{Discussion} % (fold)
+\label{sec:discussion}
 
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text.
-
+% section discussion (end)
+\newpage
+% ===================================================================================
 %% The Appendices part is started with the command \appendix;

### 2016-12-04 paper/main.tex
intro section

--- 2016-12-04 paper/main.tex
@@
 % \linenumbers
+% ===================================================================================
+\section{Introduction} % (fold)
+\label{sec:introduction}
 
+SGD is widely used.
+SGD has been viewed as Markov chain.
+No previous work has analyzed SGD as sampling technique.
+
+(sampling meth formulation)
+
+Our approach to the problem (xxx) is related to classical stochastic gradient descent algorithms [RM51, PJ92], where one assumes access to samples xx from the distribution Π and performs gradient updates using xxx.
+This reduces to the randomized incremental subgradient method of Nedi and Bertsekas􏰇 [xxxxxx] when xxx is concentrated on a set of n points, giving an objective of the form xxxxx.
+
+More generally, our problem belongs to the family of xxxxx with xxxxxx, where the goal is to xxxxxx.
+Classical analysis of SGD focus on xxxxx in nature and generally do not provide xxxxxx result.
+Our method borrows from yyyyyyy methodology [zzzzzzz], but we generalize them in that we do not assume yyyyyy.
+
+The main result of this paper is that performing stochastic gradient steps with specifically chosen step size, xxxxx results in a provably accurate and efficient sampling procedure.
+The convergence to the stationary distribution is governed by problem-dependent terms (namely the xxxx of the functions F, and xxxx) familiar from previous results on Markov chain [yyyyyy] as well as terms dependent on the rate at which xxxxxxx.
+Our xxx main theorems characterize the convergence of SGD in terms of xxxx parameter, which is xxxxx (in a sense we make precise later).
+In particular, we show that the stationary distribution is xxxxx with high probability.
+
+The remainder of the paper is organized as follows.
+The next section contains a description of the algorithm we analyze and our main technical results.
+Following that, we show that the classic stochastic gradient descent can be viewed as a special case of our algorithm in Section 3.
+We expand on these results and provide an upper bound of the mixing time throughout Section 4, and give numerical examples to compare our result with other sampling methods like xxxxxx.
+We conclude with discussion in Section 5.
+
+% section introduction (end)
+% ===================================================================================
 %% main text
@@
     \centering
-    \includegraphics{figure/case1_step_0.005_iter_1e3.png}
+    \includegraphics{../figure/case1_step_0.005_iter_1e3.png}
     \caption{Experiment 1: the empirical distribution using SGD}
@@
 \end{figure}
-
+% ===================================================================================
 \section{Sampling from posterior distribution}
@@
 Some figures...
+% ===================================================================================
+\section{Upper bound on the mixing time} % (fold)
+\label{sec:upper_bound_on_the_mixing_time}
 
-\section{Sample section}
-\label{sec1}
+% section upper_bound_on_the_mixing_time (end)
+% ===================================================================================
+\section{Numerical experiments} % (fold)
+\label{sec:numerical_experiments}
 
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-\subsection{Sample subsection}
-\label{subsec1}
+% section numerical_experiments (end)
+% ===================================================================================
+\section{Discussion} % (fold)
+\label{sec:discussion}
 
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text.
+- what we have achieved
 
+- Future work
+
+% section discussion (end)
+\newpage
+% ===================================================================================
 %% The Appendices part is started with the command \appendix;

### 2016-12-04 paper/main.tex

--- 2016-12-04 paper/main.tex
@@
 
+SGD is widely used.
+SGD has been viewed as Markov chain.
+No previous work has analyzed SGD as sampling technique.
+
+(sampling meth formulation)
+
+Our approach to the problem (xxx) is related to classical stochastic gradient descent algorithms [RM51, PJ92], where one assumes access to samples xx from the distribution Π and performs gradient updates using xxx.
+This reduces to the randomized incremental subgradient method of Nedi and Bertsekas􏰇 [xxxxxx] when xxx is concentrated on a set of n points, giving an objective of the form xxxxx.
+
+More generally, our problem belongs to the family of xxxxx with xxxxxx, where the goal is to xxxxxx.
+Classical analysis of SGD focus on xxxxx in nature and generally do not provide xxxxxx result.
+Our method borrows from yyyyyyy methodology [zzzzzzz], but we generalize them in that we do not assume yyyyyy.
+
+The main result of this paper is that performing stochastic gradient steps with specifically chosen step size, xxxxx results in a provably accurate and efficient sampling procedure.
+The convergence to the stationary distribution is governed by problem-dependent terms (namely the xxxx of the functions F, and xxxx) familiar from previous results on Markov chain [yyyyyy] as well as terms dependent on the rate at which xxxxxxx.
+Our xxx main theorems characterize the convergence of SGD in terms of xxxx parameter, which is xxxxx (in a sense we make precise later).
+In particular, we show that the stationary distribution is xxxxx with high probability.
+
+The remainder of the paper is organized as follows.
+The next section contains a description of the algorithm we analyze and our main technical results.
+Following that, we show that the classic stochastic gradient descent can be viewed as a special case of our algorithm in Section 3.
+We expand on these results and provide an upper bound of the mixing time throughout Section 4, and give numerical examples to compare our result with other sampling methods like xxxxxx.
+We conclude with discussion in Section 5.
+
 % section introduction (end)
-
 % ===================================================================================
@@
 Some figures...
+% ===================================================================================
+\section{Upper bound on the mixing time} % (fold)
+\label{sec:upper_bound_on_the_mixing_time}
 
+% section upper_bound_on_the_mixing_time (end)
 % ===================================================================================
@@
 \label{sec:discussion}
+
+- what we have achieved
+
+- Future work
 

### 2016-12-04 poster/main.tex
three col layout

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Jacobs Landscape Poster
% LaTeX Template
% Version 1.0 (29/03/13)
%
% Created by:
% Computational Physics and Biophysics Group, Jacobs University
% https://teamwork.jacobs-university.de:8443/confluence/display/CoPandBiG/LaTeX+Poster
%
% Further modified by:
% Nathaniel Johnston (nathaniel@njohnston.ca)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[final]{beamer}

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

\usetheme{confposter} % Use the confposter theme supplied with this template

\setbeamercolor{block title}{fg=ngreen,bg=white} % Colors of the block titles
\setbeamercolor{block body}{fg=black,bg=white} % Colors of the body of blocks
\setbeamercolor{block alerted title}{fg=white,bg=dblue!70} % Colors of the highlighted block titles
\setbeamercolor{block alerted body}{fg=black,bg=dblue!10} % Colors of the body of highlighted blocks
% Many more colors are available for use in beamerthemeconfposter.sty

%-----------------------------------------------------------
% Define the column widths and overall poster size
% To set effective sepwid, onecolwid and twocolwid values, first choose how many columns you want and how much separation you want between columns
% In this template, the separation width chosen is 0.024 of the paper width and a 4-column layout
% onecolwid should therefore be (1-(# of columns+1)*sepwid)/# of columns e.g. (1-(4+1)*0.024)/4 = 0.22
% Set twocolwid to be (2*onecolwid)+sepwid = 0.464
% Set threecolwid to be (3*onecolwid)+2*sepwid = 0.708

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
% \setlength{\onecolwid}{0.22\paperwidth} % Width of one column
% \setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
% \setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\onecolwid}{0.3013\paperwidth} % Width of one column
\setlength{\twocolwid}{0.6026\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.904\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

\usepackage{graphicx}  % Required for including images

\usepackage{booktabs} % Top and bottom rules for tables

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\title{A Novel Sampling Method Using Stochastic Gradient Descent} % Poster title

\author{Yu Wang and Weixin Cai} % Author(s)

\institute{Department of Statistics, UC Berkeley} % Institution(s)

%----------------------------------------------------------------------------------------

\begin{document}

\addtobeamertemplate{block end}{}{\vspace*{2ex}} % White space under blocks
\addtobeamertemplate{block alerted end}{}{\vspace*{2ex}} % White space under highlighted (alert) blocks

\setlength{\belowcaptionskip}{2ex} % White space under figures
\setlength\belowdisplayshortskip{2ex} % White space under equations

\begin{frame}[t] % The whole poster is enclosed in one beamer frame

\begin{columns}[t] % The whole poster consists of three major columns, the second of which is split into two columns twice - the [t] option aligns each column's content to the top

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The first column

%----------------------------------------------------------------------------------------
%	OBJECTIVES
%----------------------------------------------------------------------------------------

\begin{alertblock}{Objectives}

Lorem ipsum dolor sit amet, consectetur, nunc tellus pulvinar tortor, commodo eleifend risus arcu sed odio:
\begin{itemize}
\item Mollis dignissim, magna augue tincidunt dolor, interdum vestibulum urna
\item Sed aliquet luctus lectus, eget aliquet leo ullamcorper consequat. Vivamus eros sem, iaculis ut euismod non, sollicitudin vel orci.
\item Nascetur ridiculus mus.
\item Euismod non erat. Nam ultricies pellentesque nunc, ultrices volutpat nisl ultrices a.
\end{itemize}

\end{alertblock}

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

\begin{block}{Introduction}

Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit. Sed commodo molestie porta. Sed ultrices scelerisque sapien ac commodo. Donec ut volutpat elit. Sed laoreet accumsan mattis. Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem. Praesent dictum tempor pulvinar. Suspendisse potenti. Sed tincidunt varius ipsum, et porta nulla suscipit et. Etiam congue bibendum felis, ac dictum augue cursus a. \textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est. In ut orci purus, interdum ornare nibh. Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla. Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam. Maecenas sed diam augue.

This statement requires citation \cite{Smith:2012qr}.

\end{block}

%------------------------------------------------

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

%----------------------------------------------------------------------------------------

\end{column} % End of the first column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % Begin a column which is two columns wide (column 2)

%----------------------------------------------------------------------------------------
%	MATERIALS
%----------------------------------------------------------------------------------------

\begin{block}{Materials}

The following materials were required to complete the research:

\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Eu facilisis est tempus quis
\end{itemize}

The materials were prepared according to the steps outlined below:

\begin{enumerate}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Curabitur pellentesque dignissim
\end{enumerate}

\end{block}

%----------------------------------------------------------------------------------------

\end{column} % End of the second column

\begin{column}{\sepwid}\end{column} % Empty spacer column

\begin{column}{\onecolwid} % The third column

%----------------------------------------------------------------------------------------
%	CONCLUSION
%----------------------------------------------------------------------------------------

\begin{block}{Conclusion}

Nunc tempus venenatis facilisis. \textbf{Curabitur suscipit} consequat eros non porttitor. Sed a massa dolor, id ornare enim. Fusce quis massa dictum tortor \textbf{tincidunt mattis}. Donec quam est, lobortis quis pretium at, laoreet scelerisque lacus. Nam quis odio enim, in molestie libero. Vivamus cursus mi at \textit{nulla elementum sollicitudin}.

\end{block}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Additional Information}

Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\end{itemize}

\end{block}

%----------------------------------------------------------------------------------------
%   ACKNOWLEDGEMENTS
%----------------------------------------------------------------------------------------

\begin{block}{Acknowledgements}

\small{\rmfamily{Nam mollis tristique neque eu luctus. Suspendisse rutrum congue nisi sed convallis. Aenean id neque dolor. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\

\end{block}

%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------

\begin{block}{References}

\nocite{*} % Insert publications even if they are not cited in the poster
\small{\bibliographystyle{unsrt}
\bibliography{sample}\vspace{0.75in}}

\end{block}

%----------------------------------------------------------------------------------------
%	CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{block}{Contant Information}

\begin{itemize}
\item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
\item Email: \href{mailto:john@smith.com}{john@smith.com}
\item Phone: +1 (000) 111 1111
\end{itemize}

\end{block}

\begin{center}
\begin{tabular}{ccc}
\includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
\end{tabular}
\end{center}

%----------------------------------------------------------------------------------------

\end{column} % End of the third column

\end{columns} % End of all the columns in the poster

\end{frame} % End of the enclosing frame

\end{document}

### 2016-12-04 paper/main.tex
formula
Updates from ShareLaTeX

--- 2016-12-04 paper/main.tex
@@
 \newcommand{\by}{\mathbf{y}}
+\newcommand{\var}{\mathrm{var}}
 \DeclareMathOperator*{\argmin}{\arg\!\min}
@@
 \STATE
-$\bx^{k+1} \gets \bx^k - \alpha(\nabla f(\bx^k) + \epsilon^t)$;
+$\bx^{k+1} \gets \bx^k - \alpha\nabla f(\bx^k) + \epsilon^t$;
 \STATE $k\gets k+1$;
@@
 \]
-Then we could use SGD to draw sample from it. Note that we could approximate the noisy gradient step by subsampling. By central limit theorem, we know it still holds.
-
+By Conjecture 1, we could use SGD to draw samples using $(-\sum_i \log P(X_i|\theta) + \log P(\theta), \epsilon, 2\epsilon)$.  Note that the core update rule is
+\[
+\theta^{t+1} \gets \theta^{t} + \alpha (n^{-1} \sum_i \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) + \epsilon^t.
+\]
+Note that $\alpha (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) + \epsilon^t$ can be approximated by 
+\[
+\sum_{i=1}^K (K^{-1} \nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)),
+\]
+where $K$ is a constant smaller than $n$ and $\eta_i$ are IID drawn from $1,\ldots, n$. When $K\ll n$, this is much computational efficient. This relationship is elaborated in the following theorem:
 \begin{theorem}[Central limit theorem]
-
+Let $K = \alpha^{-1} \var \log P(X_1|\theta^t)$, 
+\[
+\sum_{i=1}^K (K^{-1}\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) - (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) \sim \N(0, \alpha).
+\]
 \end{theorem}
-
-Suppose we would like to draw sample from a posterior distribution
-Some figures...
+A toy example showing SGD works.
 

### 2016-12-04 poster/main.tex
poster layout complete

@@
 \usepackage{graphicx}  % Required for including images
-
 \usepackage{booktabs} % Top and bottom rules for tables
+\usepackage{amssymb}
+\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{mathrsfs}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{grffile}
 
@@
 
-\title{A Novel Sampling Method Using Stochastic Gradient Descent} % Poster title
+\title{Novel Sampling Using Stochastic Gradient Descent} % Poster title
 
@@
 
-\begin{alertblock}{Objectives}
+\begin{alertblock}{Main results}
 
-Lorem ipsum dolor sit amet, consectetur, nunc tellus pulvinar tortor, commodo eleifend risus arcu sed odio:
-\begin{itemize}
+% \centerline{ \bf{ Aim of study}}
+
+\begin{enumerate}
 \item Mollis dignissim, magna augue tincidunt dolor, interdum vestibulum urna
@@
 \item Euismod non erat. Nam ultricies pellentesque nunc, ultrices volutpat nisl ultrices a.
-\end{itemize}
+\end{enumerate}
 
@@
 
-\begin{block}{Introduction}
+\begin{block}{SGD Sampling Algorithm}
 
@@
 
+%------------------------------------------------
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{placeholder.jpg}
+\caption{Figure caption}
+\end{figure}
+
 %----------------------------------------------------------------------------------------
@@
 
-\begin{block}{Materials}
+\begin{block}{Stationary Distribution}
 
@@
 %----------------------------------------------------------------------------------------
+%   ADDITIONAL INFORMATION
+%----------------------------------------------------------------------------------------
+
+\begin{block}{SGD As Posterior Sampler}
+
+Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
+\begin{itemize}
+\item Curabitur pellentesque dignissim
+\item Eu facilisis est tempus quis
+\item Duis porta consequat lorem
+\end{itemize}
+
+\end{block}
+
+%----------------------------------------------------------------------------------------
 
@@
 \begin{column}{\onecolwid} % The third column
+
+%------------------------------------------------
+
+\begin{figure}
+\includegraphics[width=0.8\linewidth]{placeholder.jpg}
+\caption{Figure caption}
+\end{figure}
+
+%----------------------------------------------------------------------------------------
+%   ADDITIONAL INFORMATION
+%----------------------------------------------------------------------------------------
+
+\begin{block}{Upper Bound On Mixing Time}
+
+Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
+\begin{itemize}
+\item Curabitur pellentesque dignissim
+\item Eu facilisis est tempus quis
+\item Duis porta consequat lorem
+\end{itemize}
+
+\end{block}
 
@@
 Vivamus cursus mi at \textit{nulla elementum sollicitudin}.
-
-\end{block}
-
-%----------------------------------------------------------------------------------------
-%	ADDITIONAL INFORMATION
-%----------------------------------------------------------------------------------------
-
-\begin{block}{Additional Information}
-
-Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
-\begin{itemize}
-\item Curabitur pellentesque dignissim
-\item Eu facilisis est tempus quis
-\item Duis porta consequat lorem
-\end{itemize}
 
@@
 \begin{itemize}
-\item Web: \href{http://www.university.edu/smithlab}{http://www.university.edu/smithlab}
-\item Email: \href{mailto:john@smith.com}{john@smith.com}
-\item Phone: +1 (000) 111 1111
+\item Email: \href{mailto:wang.yu@berkeley.edu}{wang.yu@berkeley.edu}
+\item Email: \href{mailto:wcai@berkeley.edu}{wcai@berkeley.edu}
 \end{itemize}
@@
 \end{block}
-
-\begin{center}
-\begin{tabular}{ccc}
-\includegraphics[width=0.4\linewidth]{logo.png} & \hfill & \includegraphics[width=0.4\linewidth]{logo.png}
-\end{tabular}
-\end{center}
 

### 2016-12-04 paper/main.tex

--- 2016-12-04 paper/main.tex
@@
 \]
-Then we could use SGD to draw sample from it. Note that we could approximate the noisy gradient step by subsampling. By central limit theorem, we know it still holds.
-
+By Conjecture 1, we could use SGD to draw samples using $(-\sum_i \log P(X_i|\theta) + \log P(\theta), \epsilon, 2\epsilon)$.  Note that the core update rule is
+\[
+\theta^{t+1} \gets \theta^{t} + \alpha (n^{-1} \sum_i \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) + \epsilon^t.
+\]
+Note that $\alpha (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) + \epsilon^t$ can be approximated by 
+\[
+\sum_{i=1}^K (K^{-1} \nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)),
+\]
+where $K$ is a constant smaller than $n$ and $\eta_i$ are IID drawn from $1,\ldots, n$. When $K\ll n$, this is much computational efficient. This relationship is elaborated in the following theorem:
 \begin{theorem}[Central limit theorem]
-
+Let $K = \alpha^{-1} \var \log P(X_1|\theta^t)$, 
+\[
+\sum_{i=1}^K (K^{-1}\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) - (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) \sim \N(0, \alpha).
+\]
 \end{theorem}
 
-Suppose we would like to draw sample from a posterior distribution
-Some figures...
+A toy example showing SGD works.
 % ===================================================================================
@@
 \label{sec:numerical_experiments}
+
+$$\exp \left\{ { -x^4 } \right\}$$
+
+$$\exp \left\{ { - \left| x \right|} \right\}$$
 

### 2016-12-04 paper/main.tex
minor index

@@
     \caption{Experiment 1: the empirical histogram using SGD.
-Each column corresponds to a different number of samples ($1e3$, $1e4$, and $1e5$), each row corresponds to a different distrubtion ($f_1(x) = \exp(-x^4)$, $f_3(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$}
+Each column corresponds to a different number of samples ($1e3$, $1e4$, and $1e5$), each row corresponds to a different distrubtion ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$}
     \label{Fig:exp1}
@@
 
-$$\exp \left\{ { -x^4 } \right\}$$
+$f_1(x) = \exp(-x^4)$
 
-$$\exp \left\{ { - \left| x \right|} \right\}$$
+$f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$
+
+$f_3(x) = \exp(-|x|)$
 

### 2016-12-04 poster/main.tex
poster content

@@
 
-Lorem ipsum dolor \textbf{sit amet}, consectetur adipiscing elit.
-Sed commodo molestie porta.
-Sed ultrices scelerisque sapien ac commodo.
-Donec ut volutpat elit.
-Sed laoreet accumsan mattis.
-Integer sapien tellus, auctor ac blandit eget, sollicitudin vitae lorem.
-Praesent dictum tempor pulvinar.
-Suspendisse potenti.
-Sed tincidunt varius ipsum, et porta nulla suscipit et.
-Etiam congue bibendum felis, ac dictum augue cursus a.
-\textbf{Donec} magna eros, iaculis sit amet placerat quis, laoreet id est.
-In ut orci purus, interdum ornare nibh.
-Pellentesque pulvinar, nibh ac malesuada accumsan, urna nunc convallis tortor, ac vehicula nulla tellus eget nulla.
-Nullam lectus tortor, \textit{consequat tempor hendrerit} quis, vestibulum in diam.
-Maecenas sed diam augue.
-
-This statement requires citation \cite{Smith:2012qr}.
+\begin{algorithm}[H]
+{\small
+Given data $X_1,\ldots, X_n$, model $p(X|\theta)$, sample size $K$
+\begin{algorithmic}\caption{SGD based sampling}\label{Alg:SGD_Sampling}
+\STATE {\bf Initialize} $ \theta^0$, $t \gets 0$;
+\WHILE{stopping criterion not satisfied}
+\STATE draw $K$ iid samples with replacement from $1,\ldots, n$, denoted $\eta_1,\ldots, \eta_K$.
+\STATE calculate the mean $a^t$ and the variance $v^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
+\STATE set the stepsize $\alpha^t \gets K^{-1} v^t$
+\STATE
+$\theta^{t+1} \gets \theta^t + \alpha^ta^t$;
+\STATE $t\gets t+1$;
+\ENDWHILE
+\STATE return $\theta^k$.
+\end{algorithmic}}
+\end{algorithm}
 
@@
 \begin{figure}
-\includegraphics[width=0.8\linewidth]{placeholder.jpg}
-\caption{Figure caption}
+    \centering
+    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e5.png}\\
+    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e5.png}\\
+    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e5.png}
+    \caption{Experiment 1: the empirical histogram using SGD.
+Each column corresponds to a different number of samples ($1e3$, $1e4$, and $1e5$), each row corresponds to a different distrubtion ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$}
+    \label{Fig:exp1}
 \end{figure}

### 2016-12-04 poster/main.tex
intro section

@@
 \begin{enumerate}
-\item Mollis dignissim, magna augue tincidunt dolor, interdum vestibulum urna
-\item Sed aliquet luctus lectus, eget aliquet leo ullamcorper consequat. Vivamus eros sem, iaculis ut euismod non, sollicitudin vel orci.
-\item Nascetur ridiculus mus.
-\item Euismod non erat. Nam ultricies pellentesque nunc, ultrices volutpat nisl ultrices a.
+\item Stochastic gradient descent (SGD) as a class of efficient Markov chain sampler
+\item Proved stationary distribution
+\item Fast sampler for any Bayesian posteriors
+\item Derived upper bound on the mixing time based on convergence results
 \end{enumerate}
@@
     \centering
-    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e3.png}
-    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e4.png}
-    \includegraphics[width=.3\textwidth]{../figure/case1_step_0.005_iter_1e5.png}\\
-    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e3.png}
-    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e4.png}
-    \includegraphics[width=.3\textwidth]{../figure/case2_step_0.005_iter_1e5.png}\\
-    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e3.png}
-    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e4.png}
-    \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e5.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e5.png}\\
+    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e5.png}\\
+    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e3.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e4.png}
+    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e5.png}
     \caption{Experiment 1: the empirical histogram using SGD.

### 2016-12-05 paper/main.tex
intro

@@
 
-SGD is widely used.
-SGD has been viewed as Markov chain.
+The posterior sampling method is used to great advantage by a board range of statistical methodologies, such as EM algorithm \citep{Dempster_Maximum_1977}.
+From the Bayesian point of view, E-step of the EM algorithm can be seen as calculating the posterior distribution of the parameters of interest \citep{Tanner_The_1987}.
+Another crucial arena of posterior sampling is Bayesian modeling.
+For example, \cite{Geman_Stochastic_1993} studied image restoration as a maximum a posteriori (MAP) problem on lattice graph.
+They proposed a Markov Random Field - Gibbs class of method for solving the posterior inference.
+
+Typically, to implement such algorithms, one must be able to sample from the posterior distribution $p(\theta|y,z)$.
+In general, however, the posterior does not have closed form and sampling could be difficult and sometimes intractable.
+Various alternatives have been proposed such as Monte-Carlo method to approximate the posterior in EM algorithm \citep{Wei_A_1990}.
+\cite{Tanner_The_1987} considered data augmentation approach for calculating posterior.
+Analysis of posterior is studied in \cite{Rubin_The_1981} as a Bayesian Bootstrap approach.
+
+To formalize the goal, the observed data $y$ follows a probability distribution indexed by $\theta$ : $p(y | \theta)$. We want to generate i.i.d. samples
+\begin{equation}
+\label{eq:sample}
+x\mathop \sim\limits^{i.i.d.} p(\theta |y)
+\end{equation}
+
+Our approach to the problem (\ref{eq:sample}) is related to classical stochastic gradient descent (SGD) algorithms \citep{Robbins_A_1951,Polyak_Acceleration_1992}, where one assumes access to samples $y_1, ..., y_n$ from the distribution $p$ and performs gradient updates using $\nabla P(\theta ;y)$.
+\emph{This reduces to the randomized incremental subgradient method of \cite{Nedic_Incremental_2001} when $P$ is concentrated on a set of $n$ points, giving an objective of the form
+$p(x) = \frac{1}{n}\sum\limits_{i = 1}^n {{p_i}(x)}$.} SGD is widely applied in statistical estimation and machine learning literature \citep{LeCun_Efficient_2012,Finkel_Efficient_2008}.
+Classical analysis of SGD focus on convergence in nature and generally do not provide result on its sampling distribution.
+It is not shown until recently that SGD, under mild conditions, can be viewed as a Markov chain \citep{kushner2012stochastic,bach2014adaptivity}.
 No previous work has analyzed SGD as sampling technique.
 
-(sampling meth formulation)
-
-Our approach to the problem (xxx) is related to classical stochastic gradient descent algorithms [RM51, PJ92], where one assumes access to samples xx from the distribution Π and performs gradient updates using xxx.
-This reduces to the randomized incremental subgradient method of Nedi and Bertsekas􏰇 [xxxxxx] when xxx is concentrated on a set of n points, giving an objective of the form xxxxx.
-
-More generally, our problem belongs to the family of xxxxx with xxxxxx, where the goal is to xxxxxx.
-Classical analysis of SGD focus on xxxxx in nature and generally do not provide xxxxxx result.
-Our method borrows from yyyyyyy methodology [zzzzzzz], but we generalize them in that we do not assume yyyyyy.
-
-The main result of this paper is that performing stochastic gradient steps with specifically chosen step size, xxxxx results in a provably accurate and efficient sampling procedure.
-The convergence to the stationary distribution is governed by problem-dependent terms (namely the xxxx of the functions F, and xxxx) familiar from previous results on Markov chain [yyyyyy] as well as terms dependent on the rate at which xxxxxxx.
+The main result of this paper is that performing stochastic gradient steps with specifically chosen step size, xxxxx results in a provably accurate and efficient sampling procedure for Bayesian posteriors.
+The convergence to the stationary distribution is governed by problem-dependent terms (namely the xxxx of the functions $P$, and xxxx) familiar from previous results on Markov chain [yyyyyy] as well as terms dependent on the rate at which xxxxxxx.
 Our xxx main theorems characterize the convergence of SGD in terms of xxxx parameter, which is xxxxx (in a sense we make precise later).
@@
 The next section contains a description of the algorithm we analyze and our main technical results.
-Following that, we show that the classic stochastic gradient descent can be viewed as a special case of our algorithm in Section 3.
+Following that in Section 3, we show that the classic stochastic gradient descent can be viewed as a special case of our algorithm.
 We expand on these results and provide an upper bound of the mixing time throughout Section 4, and give numerical examples to compare our result with other sampling methods like xxxxxx.
@@
 Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$,
-\begin{algorithmic}\caption{Stochastic gradient descent}\label{Alg:SGD}
+\begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
 \STATE {\bf Initialize} $ \bx^0$ arbitrarily;
@@
 \end{theorem}
+\begin{algorithm}
+{\small
+Given data $X_1,\ldots, X_n$, model $p(X|\theta)$, sample size $K$
+\begin{algorithmic}\caption{SGD based sampling}\label{Alg:SGD_Sampling}
+\STATE {\bf Initialize} $ \theta^0$, $t \gets 0$;
+\WHILE{stopping criterion not satisfied}
+\STATE draw $K$ iid samples with replacement from $1,\ldots, n$, denoted $\eta_1,\ldots, \eta_K$.
+\STATE calculate the mean $a^t$ and the variance $v^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
+\STATE set the stepsize $\alpha^t \gets K^{-1} v^t$
+\STATE
+$\theta^{t+1} \gets \theta^t + \alpha^ta^t$;
+\STATE $t\gets t+1$;
+\ENDWHILE
+\STATE return $\theta^k$.
+\end{algorithmic}}
+\end{algorithm}
 

### 2016-12-05 paper/main.tex

@@
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\E}{\mathbb{E}}
 \newcommand{\D}{\mathscr{D}}
@@
 \STATE draw $K$ iid samples with replacement from $1,\ldots, n$, denoted $\eta_1,\ldots, \eta_K$.
-\STATE calculate the mean $a^t$ and the variance $v^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
-\STATE set the stepsize $\alpha^t \gets K^{-1} v^t$
+\STATE calculate the mean $a^t$ and the covariance matrix $\Sigma^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
 \STATE
-$\theta^{t+1} \gets \theta^t + \alpha^ta^t$;
+$\theta^{t+1} \gets \theta^t + 2(\Sigma^t)^{-1}a^t$;
 \STATE $t\gets t+1$;
@@
 \label{sec:upper_bound_on_the_mixing_time}
-
+In order to analyze the efficiency of SGD, we need to consider its mixing time.
+If SGD's mixing time is small, we know it will be a very efficient sampling method.
+How to estimate its mixing time?
+In the past literature, the upperbound of a mixing time can be obtained by a coupling technique.
+Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $d(t) = \max_{x\in \Omega} \|P^t(x, \cdot), \pi(\cdot)\|_{TV}$, and $\bar{d}(t) = \max_{x,y\in \Omega} \|P^t(x, \cdot), P^t(y,\cdot)\|_{TV}$.
+Define $t_{mix} = \min\{t:d(t) < \epsilon\}$.
+\begin{conjecture}[Upperbound for mixing time] $\tau$ is the convergence stoppiing time. $\tau_{mix} \leq 2 \max_{x} \E_{x}(\tau)$.
+\end{conjecture}
 % section upper_bound_on_the_mixing_time (end)

### 2016-12-05 paper/main.tex
complete conclusion

@@
 
-The posterior sampling method is used to great advantage by a board range of statistical methodologies, such as EM algorithm \citep{Dempster_Maximum_1977}.
+The posterior sampling method is used to great advantage by a board range of statistical methodologies, such as EM algorithm \citep{dempster1977maximum}.
 From the Bayesian point of view, E-step of the EM algorithm can be seen as calculating the posterior distribution of the parameters of interest \citep{Tanner_The_1987}.
@@
 In general, however, the posterior does not have closed form and sampling could be difficult and sometimes intractable.
-Various alternatives have been proposed such as Monte-Carlo method to approximate the posterior in EM algorithm \citep{Wei_A_1990}.
+Various alternatives have been proposed such as Monte-Carlo method to approximate the posterior in EM algorithm \citep{Wei1990}.
 \cite{Tanner_The_1987} considered data augmentation approach for calculating posterior.
@@
 
-Our approach to the problem (\ref{eq:sample}) is related to classical stochastic gradient descent (SGD) algorithms \citep{Robbins_A_1951,Polyak_Acceleration_1992}, where one assumes access to samples $y_1, ..., y_n$ from the distribution $p$ and performs gradient updates using $\nabla P(\theta ;y)$.
-\emph{This reduces to the randomized incremental subgradient method of \cite{Nedic_Incremental_2001} when $P$ is concentrated on a set of $n$ points, giving an objective of the form
-$p(x) = \frac{1}{n}\sum\limits_{i = 1}^n {{p_i}(x)}$.} SGD is widely applied in statistical estimation and machine learning literature \citep{LeCun_Efficient_2012,Finkel_Efficient_2008}.
+Our approach to the problem (\ref{eq:sample}) is related to classical stochastic gradient descent (SGD) algorithms \citep{Robbins_A_1951,Polyak_Acceleration_1992}, where one assumes access to samples $y_1, ..., y_n$ from the distribution $p$ and performs gradient updates using $\nabla \log p(\theta ;y)$.
+SGD is widely applied in statistical estimation and machine learning literature \citep{lecun2012efficient,Finkel_Efficient_2008}.
 Classical analysis of SGD focus on convergence in nature and generally do not provide result on its sampling distribution.
-It is not shown until recently that SGD, under mild conditions, can be viewed as a Markov chain \citep{kushner2012stochastic,bach2014adaptivity}.
-No previous work has analyzed SGD as sampling technique.
+Although it is shown that SGD, under mild conditions, can be viewed as a Markov chain \citep{kushner2012stochastic,bach2014adaptivity}.
+Very few previous work has analyzed SGD as sampling technique.
+When compared with other sampling methods like Metropolis-Hastings \citep{Metropolis1953}, our method utilizes only a subset of the dataset to calculate transition probability, while Metropolis-Hastings requires all samples to construct likelihood $p(x|\theta)$ and subsequently the posterior.
+This makes our approach more applicable to ``Big Data'' problems, when the sample size is usually in the order of millions, or even billions.
+Our method is also distinct from Metropolis-Hastings, a likelihood-based sampler, in that the SGD sampler is entirely based on the gradient of the target distribution.
 
-The main result of this paper is that performing stochastic gradient steps with specifically chosen step size, xxxxx results in a provably accurate and efficient sampling procedure for Bayesian posteriors.
-The convergence to the stationary distribution is governed by problem-dependent terms (namely the xxxx of the functions $P$, and xxxx) familiar from previous results on Markov chain [yyyyyy] as well as terms dependent on the rate at which xxxxxxx.
-Our xxx main theorems characterize the convergence of SGD in terms of xxxx parameter, which is xxxxx (in a sense we make precise later).
-In particular, we show that the stationary distribution is xxxxx with high probability.
+The main result of this paper is that performing stochastic gradient steps with specifically chosen objective function, step size, and sampling rate results in a provably accurate and efficient sampling procedure for Bayesian posteriors.
+The convergence to the stationary distribution is governed by problem-dependent terms (namely the expected convergence time of SGD) familiar from previous results on Markov chain \citep{aldous2002reversible,levin2009markov}.
+Our xxx main results characterize the sampling distribution of SGD.
+In particular, we show that the sampling distribution converges to the desired distribution with high probability.
 
@@
 The next section contains a description of the algorithm we analyze and our main technical results.
-Following that in Section 3, we show that the classic stochastic gradient descent can be viewed as a special case of our algorithm.
-We expand on these results and provide an upper bound of the mixing time throughout Section 4, and give numerical examples to compare our result with other sampling methods like xxxxxx.
+Following that in Section 3, we show that the classic stochastic gradient descent can be viewed as a special case of our algorithm, and give numerical examples to demonstrate our result.
+We expand on these results and provide an upper bound of the mixing time throughout Section 4.
 We conclude with discussion in Section 5.
@@
 % section upper_bound_on_the_mixing_time (end)
+
 % ===================================================================================
-\section{Numerical experiments} % (fold)
-\label{sec:numerical_experiments}
+\section{Discussion} % (fold)
+\label{sec:discussion}
 
@@
 $f_3(x) = \exp(-|x|)$
-
-% section numerical_experiments (end)
-% ===================================================================================
-\section{Discussion} % (fold)
-\label{sec:discussion}
 

### 2016-12-05 poster/main.tex
poster initial

@@
 
-\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
+% \usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
+\usepackage[scale=0.8]{beamerposter}
 
@@
 \newlength{\threecolwid}
-\setlength{\paperwidth}{48in} % A0 width: 46.8in
-\setlength{\paperheight}{36in} % A0 height: 33.1in
+% \setlength{\paperwidth}{48in} % A0 width: 46.8in
+% \setlength{\paperheight}{36in} % A0 height: 33.1in
+\setlength{\paperwidth}{36in} % A0 width: 46.8in
+\setlength{\paperheight}{24in} % A0 height: 33.1in
 \setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
@@
 
+\newcommand{\bx}{\mathbf{x}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\E}{\mathbb{E}}
+\newcommand{\D}{\mathscr{D}}
+\newcommand{\N}{\mathscr{N}}
+\newcommand{\by}{\mathbf{y}}
+\newcommand{\var}{\mathrm{var}}
+\DeclareMathOperator*{\argmin}{\arg\!\min}
+
+\newtheorem{conjecture}{Conjecture}
+% \newtheorem{theorem}{Theorem}
+\newtheorem{experiment}{Experiment}
+
+% inline theorem
+\makeatletter
+\setbeamertemplate{theorem begin}
+  {\usebeamercolor[fg]{thcolor}% for the heading
+  {\bfseries\inserttheoremname~}%
+  \ifx\inserttheoremaddition\@empty\else(\inserttheoremaddition)\ \fi%
+  \hspace{.01em}\normalfont\usebeamercolor[fg]{thcolor}% for the body
+  }
+\setbeamertemplate{theorem end}{}
+\makeatother
 %----------------------------------------------------------------------------------------
@@
 %----------------------------------------------------------------------------------------
+%   MOTIVATION
+%----------------------------------------------------------------------------------------
+
+\begin{block}{Motivation}
+
+\begin{itemize}
+    \item aaa
+\end{itemize}
+
+\end{block}
+
+%------------------------------------------------
+%
+%----------------------------------------------------------------------------------------
 %	INTRODUCTION
@@
 {\small
-Given data $X_1,\ldots, X_n$, model $p(X|\theta)$, sample size $K$
-\begin{algorithmic}\caption{SGD based sampling}\label{Alg:SGD_Sampling}
-\STATE {\bf Initialize} $ \theta^0$, $t \gets 0$;
+Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$,
+\begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
+\STATE {\bf Initialize} $ \bx^0$ arbitrarily;
 \WHILE{stopping criterion not satisfied}
-\STATE draw $K$ iid samples with replacement from $1,\ldots, n$, denoted $\eta_1,\ldots, \eta_K$.
-\STATE calculate the mean $a^t$ and the variance $v^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
-\STATE set the stepsize $\alpha^t \gets K^{-1} v^t$
+\STATE draw $\epsilon^t$ from Gaussian distribution $\N(0, \sigma^2)$.
 \STATE
-$\theta^{t+1} \gets \theta^t + \alpha^ta^t$;
-\STATE $t\gets t+1$;
+$\bx^{k+1} \gets \bx^k - \alpha\nabla f(\bx^k) + \epsilon^t$;
+\STATE $k\gets k+1$;
 \ENDWHILE
-\STATE return $\theta^k$.
+\STATE return $\bx^k$.
 \end{algorithmic}}
@@
 \end{block}
-
-%------------------------------------------------
-
-\begin{figure}
-\includegraphics[width=0.8\linewidth]{placeholder.jpg}
-\caption{Figure caption}
-\end{figure}
 
@@
 
-The following materials were required to complete the research:
-
-\begin{itemize}
-\item Curabitur pellentesque dignissim
-\item Eu facilisis est tempus quis
-\item Duis porta consequat lorem
-\item Eu facilisis est tempus quis
-\end{itemize}
-
-The materials were prepared according to the steps outlined below:
-
-\begin{enumerate}
-\item Curabitur pellentesque dignissim
-\item Eu facilisis est tempus quis
-\item Duis porta consequat lorem
-\item Curabitur pellentesque dignissim
-\end{enumerate}
+\begin{conjecture}
+For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, 2\epsilon)$.
+\end{conjecture}
 
@@
 
-Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
-\begin{itemize}
-\item Curabitur pellentesque dignissim
-\item Eu facilisis est tempus quis
-\item Duis porta consequat lorem
-\end{itemize}
+\begin{theorem}[Central limit theorem]
+Let $K = \alpha^{-1} \var \log P(X_1|\theta^t)$,
+\[
+\sum_{i=1}^K (K^{-1}\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) - (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) \sim \N(0, \alpha).
+\]
+\end{theorem}
+
+A toy example showing SGD works.
 
@@
 \begin{figure}
-\includegraphics[width=0.8\linewidth]{placeholder.jpg}
+\includegraphics[width=0.4\linewidth]{../figure/simulation2_empirical.png}
+\includegraphics[width=0.4\linewidth]{../figure/simulation2_real.png}
 \caption{Figure caption}

### 2016-12-05 poster/main.tex
initial fill

@@
 
-Nunc tempus venenatis facilisis.
-\textbf{Curabitur suscipit} consequat eros non porttitor.
-Sed a massa dolor, id ornare enim.
-Fusce quis massa dictum tortor \textbf{tincidunt mattis}.
-Donec quam est, lobortis quis pretium at, laoreet scelerisque lacus.
-Nam quis odio enim, in molestie libero.
-Vivamus cursus mi at \textit{nulla elementum sollicitudin}.
+\begin{itemize}
+    \item aaa
+\end{itemize}
 

### 2016-12-05 poster/main.tex
acknowledge

@@
 
-\small{\rmfamily{Nam mollis tristique neque eu luctus.
-Suspendisse rutrum congue nisi sed convallis.
-Aenean id neque dolor.
-Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.}} \\
+\small{\rmfamily{We would like to thank Professor Martin Wainwright for his inspiring teaching this semster.
+And we also greatly appreciate Arturo Fernandez and Jeffery Chan, our GSIs, for their devotion in this course.}} \\
 

### 2016-12-05 poster/main.tex
complete content

@@
 \begin{itemize}
-    \item aaa
+\item Sampling from posterior distribution is crucial in various statistical techniques
+\item Posterior can be hard to sample  (hurdle a lot of applications)
+\item SGD can be viewed as a Markov chain
+\item Property as a Markov chain seems to be largely overlooked
+\item Stationary distribution? Mixing time? Mixing time relationship with convergence rate?
 \end{itemize}
@@
 \begin{figure}
-\includegraphics[width=0.4\linewidth]{../figure/simulation2_empirical.png}
-\includegraphics[width=0.4\linewidth]{../figure/simulation2_real.png}
+\includegraphics[width=0.5\linewidth]{../figure/simulation2_empirical.png}
+\includegraphics[width=0.5\linewidth]{../figure/simulation2_real.png}
 \caption{Figure caption}
@@
 \begin{itemize}
-    \item aaa
+\item Proposed fast SGD sampler for posterior distributions. Computing the likelihood from the full data is intensive.
+\item Proved accurate stationary distribution based on oracle results
+\item Established connection between SGD and maximize \emph{a posteriori} (MAP)
+\item Derived upper bound on mixing time
+\item Future work: Finite sample rates of convergence for the mixing time
 \end{itemize}

### 2016-12-05 poster/main.tex
complete bib
update the Algorithm

@@
 \item Stochastic gradient descent (SGD) as a class of efficient Markov chain sampler
-\item Proved stationary distribution
+\item Derived the stationary distribution
 \item Fast sampler for any Bayesian posteriors
@@
 %----------------------------------------------------------------------------------------
-
+Suppose we would like to sample from a distribution $p(x) \propto f(x)$. 
 \begin{block}{SGD Sampling Algorithm}
@@
 {\small
-Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$,
+Given $f(x)$, 
 \begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
 \STATE {\bf Initialize} $ \bx^0$ arbitrarily;
-\WHILE{stopping criterion not satisfied}
-\STATE draw $\epsilon^t$ from Gaussian distribution $\N(0, \sigma^2)$.
+\WHILE{burn-in period}
+\STATE draw $a^t$ from Gaussian distribution $\N(\nabla f(\bx^k), \Sigma^{t})$.
 \STATE
-$\bx^{k+1} \gets \bx^k - \alpha\nabla f(\bx^k) + \epsilon^t$;
+$\bx^{k+1} \gets \bx^k - (\Sigma^t)^{-1} a^t$;
 \STATE $k\gets k+1$;
@@
 \end{algorithm}
+
+\end{block}
+
+%----------------------------------------------------------------------------------------
+%   REFERENCES
+%----------------------------------------------------------------------------------------
+
+\begin{block}{References}
+
+\nocite{*} % Insert publications even if they are not cited in the poster
+\small{\bibliographystyle{unsrt}
+\bibliography{sample}\vspace{0.75in}}
 
@@
 %----------------------------------------------------------------------------------------
-%	REFERENCES
-%----------------------------------------------------------------------------------------
-
-\begin{block}{References}
-
-\nocite{*} % Insert publications even if they are not cited in the poster
-\small{\bibliographystyle{unsrt}
-\bibliography{sample}\vspace{0.75in}}
-
-\end{block}
-
-%----------------------------------------------------------------------------------------
 %	CONTACT INFORMATION
@@
 \begin{itemize}
-\item Email: \href{mailto:wang.yu@berkeley.edu}{wang.yu@berkeley.edu}
-\item Email: \href{mailto:wcai@berkeley.edu}{wcai@berkeley.edu}
+\item Email: \href{mailto:wang.yu@berkeley.edu, wcai@berkeley.edu}{\{wang.yu, wcai\}@berkeley.edu}
 \end{itemize}

### 2016-12-05 poster/main.tex
update algorithm
update the figure 1

@@
 %----------------------------------------------------------------------------------------
+
+\begin{block}{SGD Sampling Algorithm}
 Suppose we would like to sample from a distribution $p(x) \propto f(x)$. 
-\begin{block}{SGD Sampling Algorithm}
-
 \begin{algorithm}[H]
@@
 \WHILE{burn-in period}
-\STATE draw $a^t$ from Gaussian distribution $\N(\nabla f(\bx^k), \Sigma^{t})$.
+\STATE draw $a^t$ from Gaussian distribution $\N(\nabla \log f(\bx^k), \Sigma^{t})$.
 \STATE
-$\bx^{k+1} \gets \bx^k - (\Sigma^t)^{-1} a^t$;
+$\bx^{k+1} \gets \bx^k + (2\Sigma^t)^{-1} a^t$;
 \STATE $k\gets k+1$;
@@
     \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e5.png}
-    \caption{Experiment 1: the empirical histogram using SGD.
-Each column corresponds to a different number of samples ($1e3$, $1e4$, and $1e5$), each row corresponds to a different distrubtion ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$}
+    \caption{Empirical stationary distribution using SGD.
+Different columns correspond to different samples sizes ($1e3$, $1e4$, and $1e5$).
+Different rows correspond to different distributions ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$.}
     \label{Fig:exp1}
@@
 \begin{block}{Stationary Distribution}
-
 \begin{conjecture}

### 2016-12-05 poster/main.tex
update the mid column

@@
 \newcommand{\var}{\mathrm{var}}
+\newcommand{\cov}{\mathrm{cov}}
 \DeclareMathOperator*{\argmin}{\arg\!\min}
@@
 \begin{block}{SGD Sampling Algorithm}
-Suppose we would like to sample from a distribution $p(x) \propto f(x)$. 
+Suppose we would like to sample from a distribution $p(\bx)\in \D(\R^p) \propto f(\bx)$. 
 \begin{algorithm}[H]
@@
 %----------------------------------------------------------------------------------------
-
 \begin{block}{Stationary Distribution}
-\begin{conjecture}
-For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, 2\epsilon)$.
-\end{conjecture}
-
+Will Algorithm 1 converge to the desired stationary distribution? Denote $p(\bx^{t+1}|\bx^t)$ to be the density function to obtain $\bx^{t+1}$ from $\bx^{t}$. 
+The detailed balance condition holds approximately when $\|(\Sigma^t)^{-1}\|$ is small, i.e.,
+\[
+f(\bx^{t})p(\bx^{t+1}|\bx^t) = f(\bx^{t+1})p(\bx^{t}|\bx^{t+1}) ( 1 + O(\|(\Sigma^t)^{-1}\|^2)).
+\]
+That implies $f(\cdot)$ is indeed the stationary distribution of Algorithm 1. Simulation results can be found in Figure 1.
 \end{block}
@@
 \begin{block}{SGD As Posterior Sampler}
-
+When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
+\[
+p(\theta) = \prod_{i=1}^n P(X_i|\theta) P(\theta),
+\]
+The noisy gradient step in Algorithm 1 can be estimated by subsampling:
 \begin{theorem}[Central limit theorem]
-Let $K = \alpha^{-1} \var \log P(X_1|\theta^t)$,
+Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
 \[
-\sum_{i=1}^K (K^{-1}\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) - (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) \sim \N(0, \alpha).
+K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
 \]
@@
 
-A toy example showing SGD works.
+See Figure 2 for the simulation result.
 
@@
 \begin{block}{Upper Bound On Mixing Time}
-
-Maecenas ultricies feugiat velit non mattis. Fusce tempus arcu id ligula varius dictum.
-\begin{itemize}
-\item Curabitur pellentesque dignissim
-\item Eu facilisis est tempus quis
-\item Duis porta consequat lorem
-\end{itemize}
+Mixing time correspon
 

### 2016-12-05 poster/main.tex
update last column

@@
 
-\begin{block}{SGD As Posterior Sampler}
+\begin{block}{SGD As Fast Posterior Sampler}
 When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
@@
 \includegraphics[width=0.5\linewidth]{../figure/simulation2_real.png}
-\caption{Figure caption}
+\caption{The empirical/real density for $(\mu, \sigma^2)$ where $p(X_1|\mu, \sigma^2)\sim \N(\mu, \sigma^2)$, data $X_1,\ldots, X_{1000}$ is drawn from $\N(0, 1)$, $K = 1000$, sample size is $1000$.
+The empirical density is close to the real density.
+Note that variance $\sigma^2$ has higher variance than the expectation $\mu$}
 \end{figure}
@@
 \begin{block}{Upper Bound On Mixing Time}
-Mixing time correspon
-
+How effective Algorithm 1 is as a sampling method? Denote $\|\cdot\|_{\mathrm{TV}}$ the TV norm and $P^t(\bx^0)$ the density of $\bx^t$ starting from $\bx^0$. Define its mixing time to be 
+\[
+\tau_{\mathrm{mix}} \triangleq \min\{t|\max_{\bx^0}\|P^t(\bx^0) - p\|_{\mathrm{TV}}\leq 1/4\}.
+\]
+Suppose $\tau_{\bx^0}$ is the stopping time when the algorithm converges to global minimum starting from $\bx^0$, we might be able to have a upper bound for $\tau_{\mathrm{mix}}$.
+\[
+\tau_{\mathrm{mix}} \leq 4 \max_{\bx^0}\E \tau_{\bx^0}.
+\]
+So when SGD converges fast, it will also be efficient as a sampling method.
 \end{block}
@@
 \begin{itemize}
-\item Proposed fast SGD sampler for posterior distributions. Computing the likelihood from the full data is intensive.
+\item Proposed fast SGD sampler for posterior distributions when computing the likelihood using full data is intensive
 \item Proved accurate stationary distribution based on oracle results
@@
 
-\begin{block}{Contant Information}
+\begin{block}{Contact Information}
 

### 2016-12-05 poster/main.tex
finish the revision

@@
 \item Posterior can be hard to sample  (hurdle a lot of applications)
-\item SGD can be viewed as a Markov chain
-\item Property as a Markov chain seems to be largely overlooked
-\item Stationary distribution? Mixing time? Mixing time relationship with convergence rate?
+\item SGD can be viewed as a Markov chain sampler, very efficient for posterior
+\item Property as a Markov chain largely overlooked
+\item Mixing time's relationship with its convergence rate?
 \end{itemize}
@@
 The noisy gradient step in Algorithm 1 can be estimated by subsampling:
-\begin{theorem}[Central limit theorem]
+(Central limit theorem)
 Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
@@
 \]
-\end{theorem}
 

### 2016-12-05 poster/main.tex
final format

@@
 
-% \usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
-\usepackage[scale=0.8]{beamerposter}
+\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
+% \usepackage[scale=0.8]{beamerposter}
 
@@
 \newlength{\threecolwid}
-% \setlength{\paperwidth}{48in} % A0 width: 46.8in
-% \setlength{\paperheight}{36in} % A0 height: 33.1in
-\setlength{\paperwidth}{36in} % A0 width: 46.8in
-\setlength{\paperheight}{24in} % A0 height: 33.1in
+\setlength{\paperwidth}{48in} % A0 width: 46.8in
+\setlength{\paperheight}{36in} % A0 height: 33.1in
+% \setlength{\paperwidth}{36in} % A0 width: 46.8in
+% \setlength{\paperheight}{24in} % A0 height: 33.1in
 \setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
@@
     \centering
-    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e3.png}
-    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e4.png}
-    \includegraphics[width=.3\onecolwid]{../figure/case1_step_0.005_iter_1e5.png}\\
-    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e3.png}
-    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e4.png}
-    \includegraphics[width=.3\onecolwid]{../figure/case2_step_0.005_iter_1e5.png}\\
-    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e3.png}
-    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e4.png}
-    \includegraphics[width=.3\onecolwid]{../figure/case3_step_0.005_iter_1e5.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case1_step_0.005_iter_1e3.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case1_step_0.005_iter_1e4.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case1_step_0.005_iter_1e5.png}\\
+    \includegraphics[width=.33\onecolwid]{../figure/case2_step_0.005_iter_1e3.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case2_step_0.005_iter_1e4.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case2_step_0.005_iter_1e5.png}\\
+    \includegraphics[width=.33\onecolwid]{../figure/case3_step_0.005_iter_1e3.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case3_step_0.005_iter_1e4.png}
+    \includegraphics[width=.33\onecolwid]{../figure/case3_step_0.005_iter_1e5.png}
     \caption{Empirical stationary distribution using SGD.
@@
 \item Proved accurate stationary distribution based on oracle results
-\item Established connection between SGD and maximize \emph{a posteriori} (MAP)
+\item Established connection between SGD and maximize \emph{a posteriori}
 \item Derived upper bound on mixing time

### 2016-12-05 code/temp/calc_grad.py

@@ -1,0 +1,22 @@
+import numpy as np
+
+theta = np.asarray([0, 1]) # first element is mu, second is sigma^2
+data = np.reshape(np.random.randn(1000), (-1, 1))
+data = np.array([.5, 1])
+data.shape
+
+K = 100
+d = 2
+candidates = np.random.choice(1000, K, replace = True)
+
+
+def calc_grad(data, theta, candidates = np.array(range(0, data.shape[0]))):
+    mu = theta[0]
+    sigma2 = theta[1]
+    out1 = (data[candidates,:] - mu) / sigma2 * 2
+    out2 = out1**2/4 - 1/sigma2
+
+    grads = np.column_stack((out1, out2))
+    return grads
+
+calc_grad(data, theta, candidates)

### 2016-12-07 code/final/convergence.py
final ver code

@@ -1,5 +1,5 @@
 import numpy as np
-import matplotlib.pyplot as plt
+# import matplotlib.pyplot as plt
 import random
 import scipy as sp
 import statsmodels as sm

### 2016-12-07 code/final/proof_of_concept.py

@@ -1,6 +1,6 @@
 #Gradient Descent
 import numpy as np
-import matplotlib.pyplot as plt
+# import matplotlib.pyplot as plt
 import random
 # ========================================================================================
 # SGD

### 2016-12-07 code/final/simulation.py

@@ -1,5 +1,5 @@
 import numpy as np
-import matplotlib.pyplot as plt
+# import matplotlib.pyplot as plt
 import random
 import scipy as sp
 import statsmodels as sm
@@ -21,7 +21,7 @@ def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-
 
 # $ ipcluster start -n 3
 # $ ipcluster start -n 24
-def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100):
+def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, burn_in = 1e3):
     clients = ipyparallel.Client()
     dview = clients.direct_view()
 
@@ -58,6 +58,9 @@ def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noise
 
     # remove the empty column
     all_traject = np.delete(all_traject, 0, axis=1)
+    # remove burn in period
+    all_traject = all_traject[int(burn_in):,:]
+
     return all_traject
 
 # %time all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)

### 2016-12-07 code/final/1_1/mixing.py
prepare for cluster

@@ -1,0 +1,138 @@
+import numpy as np
+# import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
+import pickle
+
+def graph(formula, x_range = range(-3, 3)):
+    '''graph any function within a range
+
+    Parameters
+    ----------
+    formula : TYPE
+        The formula
+    x_range : TYPE, optional
+        The x range
+    '''
+    # x = np.array(x_range)
+    x = np.linspace(start = x_range[0], stop = x_range[len(x_range)-1], num=50, endpoint=True)
+    y = formula(x)  # <- note now we're calling the function 'formula' with x
+    plt.plot(x, y)
+    plt.show()
+# ====================================================================================
+# def pdf_to_cdf(pdf_func, a = -3, b = 3, dx = .01):
+#     # WILSON: from -inf to a: the mass is missing
+#     X  = np.arange(a,b,dx)
+#     Y  = pdf_func(X)
+#     Y /= (dx*Y).sum()
+#     CY = np.cumsum(Y*dx)
+#     step = sm.distributions.empirical_distribution.StepFunction(x = X, y = CY,side='left')
+#     return step
+
+def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
+    # WILSON: from -inf to a: the mass is missing
+    X  = np.arange(a,b,dx)
+    Y  = pdf_func(X)
+    Y /= (dx*Y).sum()
+    step = sm.distributions.empirical_distribution.StepFunction(x = X, y = Y,side='left')
+    return step
+
+# def l1(cdf1, cdf2, a=-3, b=3, dx=.01):
+#     X  = np.arange(a,b,dx)
+#     val1 = cdf1(X)
+#     val2 = cdf2(X)
+#     return np.mean(abs(val1 - val2))
+# ====================================================================================
+# plt.figure()
+# graph(ecdf, range(-3, 3))
+# graph(station_cdf, range(-3, 3))
+def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
+    # ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    X  = np.arange(a,b,dx)
+    kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
+    e_pdf = kde.evaluate(X) # vector of pdf value
+
[…]

### 2016-12-07 code/final/1_3/simulation.py

@@ -1,0 +1,66 @@
+import numpy as np
+# import matplotlib.pyplot as plt
+import random
+import scipy as sp
+import statsmodels as sm
+import ipyparallel
+
+def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, verbose = False):
+    trajectory_all = []
+    image_all = []
+    haltIter_all = []
+    for it in range(0,n_sim):
+        print(it)
+        trajectory, image, haltIter = sgd_base.GD(func, grad, initialPoint=initialPoint, stepsize=stepsize,
+                                 noiseLevel=noiseLevel, maxIter=maxIter, desiredObj=desiredObj, verbose = verbose)
+        trajectory_all.append(trajectory)
+        image_all.append(image)
+        haltIter_all.append(haltIter)
+    return trajectory_all, image_all, haltIter_all
+
+
+# $ ipcluster start -n 3
+# $ ipcluster start -n 24
+def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, burn_in = 1e3):
+    clients = ipyparallel.Client()
+    dview = clients.direct_view()
+
+    # # sync_imports does not support
+    # # import foo as bar
+    # # therefore need rewrite module names
+    # with dview.sync_imports():
+    #     import numpy as np
+    #     import matplotlib.pyplot as plt
+    #     import random
+    #     import proof_of_concept as sgd_base
+    #     import mixing as mixing
+    #     import convergence as convergence
+
+    # parallel cannot use lambda function either
+
+    dview.execute('import numpy as np')
+    dview.execute('import matplotlib.pyplot as plt')
+    dview.execute('import random')
+    dview.execute('import proof_of_concept as sgd_base')
+    dview.execute('import mixing as mixing')
+    dview.execute('import convergence as convergence')
+
+    dview.push(dict(func = func, grad = grad))
+
+    n_core = len(clients.ids)
+    n_sim_each = int(np.floor(n_sim/n_core))
+
+    results = dview.map_sync(simu_all, [n_sim_each]*n_core, [func]*n_core, [grad]*n_core)
+
+    all_traject = np.empty(shape = maxIter)
+    for it_tuple in results:
[…]

### 2016-12-07 code/final/1_4/proof_of_concept.py

@@ -1,0 +1,144 @@
+#Gradient Descent
+import numpy as np
+# import matplotlib.pyplot as plt
+import random
+# ========================================================================================
+# SGD
+# ========================================================================================
+def GD(objective, gradient, initialPoint, stepsize, noiseLevel, maxIter, desiredObj,
+       seed = None,
+       verbose = True):
+    '''
+    Perform stochastic gradient descent to maximize objective.
+
+    Args:
+    objective    - function handle, return objective
+    gradient     - function handle, return gradient
+    initialPoint - array of dimension d, starting point
+    stepsize     - numeric,
+    noiseLevel   - numeric, the variance of the Gaussian noise
+    maxIter      - integer, the iterations
+    desiredObj   - double, the desired objective function value (algorithm halts when it is reached)
+    verbose      - boolean, whether to print intermediate results
+
+    Returns:
+    trajectory   - 2d array of maxIter * d, the record of x
+    image        - 2d array of maxIter * 1, the record of objective
+    haltIter     - integer, the stopped iteration
+    '''
+    # initial config
+    if isinstance(initialPoint, float):
+        d = 1
+    else:
+        d = len(initialPoint)
+    rng = random.Random()
+    if seed is not None:
+        rng.seed(seed)
+
+    trajectory = np.zeros((maxIter, d))
+    image      = np.zeros((maxIter, 1))
+    x          = initialPoint
+    trajectory[0] = x
+    image[0]      = objective(x)
+
+    for iter in range(1, maxIter):
+        # SGD step
+        # add noise to the true gradient
+        noise = rng.normalvariate(0, noiseLevel)
+        # WILSON?: stepsize * (gradient(x) + noise)
+        x = x + stepsize * gradient(x) + noise
+        trajectory[iter] = x
+        image[iter] = objective(x)
+        if image[iter] > desiredObj:
+            if verbose:
+                print('Reached desired Objective at step %d' % iter)
+            break
+    if verbose and image[iter] < desiredObj:
+        print('Did not converge while max iteration reached %d' % iter)
+    haltIter = iter
+    return trajectory, image, haltIter
+
+# ========================================================================================
[…]

### 2016-12-07 code/final/mixing.py

@@ -1,108 +1,0 @@
-import numpy as np
-# import matplotlib.pyplot as plt
-import random
-import scipy as sp
-import statsmodels as sm
-
-def graph(formula, x_range = range(-3, 3)):
-    '''graph any function within a range
-
-    Parameters
-    ----------
-    formula : TYPE
-        The formula
-    x_range : TYPE, optional
-        The x range
-    '''
-    # x = np.array(x_range)
-    x = np.linspace(start = x_range[0], stop = x_range[len(x_range)-1], num=50, endpoint=True)
-    y = formula(x)  # <- note now we're calling the function 'formula' with x
-    plt.plot(x, y)
-    plt.show()
-# ====================================================================================
-def pdf_to_cdf(pdf_func, a = -3, b = 3, dx = .01):
-    # WILSON: from -inf to a: the mass is missing
-    X  = np.arange(a,b,dx)
-    Y  = pdf_func(X)
-    Y /= (dx*Y).sum()
-    CY = np.cumsum(Y*dx)
-    step = sm.distributions.empirical_distribution.StepFunction(x = X, y = CY,side='left')
-    return step
-
-def cdf_l1(cdf1, cdf2, a=-3, b=3, dx=.01):
-    X  = np.arange(a,b,dx)
-    val1 = cdf1(X)
-    val2 = cdf2(X)
-    return np.mean(abs(val1 - val2))
-# ====================================================================================
-# plt.figure()
-# graph(ecdf, range(-3, 3))
-# graph(station_cdf, range(-3, 3))
-
-def is_mix(emp_samples, station_func, epsilon_norm = 1e-2, a= -3, b=3, dx=.01):
-    """determine from a sample, whether it is mixing with the true distribution
-
-    Determines if mix.
-
-    Parameters
-    ----------
-    emp_samples : vec
-        The emp samples
-    station_func : func
-        The stationart distribution
-    epsilon_norm : float, optional
-        The epsilon tolerance for norm
-    a : int, optional
-        Description
-    b : int, optional
-        Description
-    dx : float, optional
-        Description
-
-    Returns
-    -------
-    bool
-        True if mix, False otherwise.
-    """
-    ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
-    station_cdf = pdf_to_cdf(pdf_func = station_func, a=a, b=b, dx=dx)
-
[…]

### 2016-12-07 code/final/2_2/simulation.py
everything 1e4

@@ -5,7 +5,7 @@ import scipy as sp
 import statsmodels as sm
 import ipyparallel
 
-def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, verbose = False):
+def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e4), desiredObj = 100, verbose = False):
     trajectory_all = []
     image_all = []
     haltIter_all = []
@@ -21,7 +21,7 @@ def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-
 
 # $ ipcluster start -n 3
 # $ ipcluster start -n 24
-def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, burn_in = 1e3):
+def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e4), desiredObj = 100, burn_in = 1e3):
     clients = ipyparallel.Client()
     dview = clients.direct_view()
 
@@ -63,4 +63,4 @@ def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noise
 
     return all_traject
 
-# %time all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
+# %time all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e4), desiredObj=100)

### 2016-12-07 code/final/1_4/mixing.py
fix odd power

@@ -126,7 +126,7 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
     # plt.savefig('yo.pdf', format='pdf')
 
     pickle.dump(obj = l1_all, file = open('./l1_all.pickle', 'wb'), protocol=pickle.HIGHEST_PROTOCOL)
-    # l1_all = pickle.load('l1_all.pickle')
+    # l1_all = pickle.load(open('l1_all.pickle', 'rb'))
 
     is_mix = l1_all <= epsilon_norm
 

### 2016-12-07 paper/main.tex

@@
 
-$f_1(x) = \exp(-x^4)$
-
-$f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$
-
-$f_3(x) = \exp(-|x|)$
-
-- what we have achieved
-
-- Future work
+In this paper, we have shown that stochastic gradient descent approaches extend in an elegant way to a sampler for posterior distributions when computing the likelihood from the full data is intensive.
+We are able to establish the stationary distribution of the procedure and gave several examples showing the accuracy and uses of our result.
+By taking a Bayesian route, we are able to show that the SGD algorithm is a sampler of a posterior under a non-informative prior.
+This enables us to establish connection between SGD and maximum \emph{a posteriori} (MAP) procedure, which is an analogy to gradient descent solving a maximum likelihood estimator in the frequentist paradigm.
+A natural extension of this work, which we hope to be able to accomplish, is to derive finite sample rates of convergence for the mixing time, which would allow a more rigor understanding of the SGD family as a whole.
+Extensive simulation of the methodology is also needed to fully understand this novel SGD sampler.
 

### 2016-12-07 poster/main.tex

@@
 % inline theorem
-\makeatletter
-\setbeamertemplate{theorem begin}
-  {\usebeamercolor[fg]{thcolor}% for the heading
-  {\bfseries\inserttheoremname~}%
-  \ifx\inserttheoremaddition\@empty\else(\inserttheoremaddition)\ \fi%
-  \hspace{.01em}\normalfont\usebeamercolor[fg]{thcolor}% for the body
-  }
-\setbeamertemplate{theorem end}{}
-\makeatother
+% \makeatletter
+% \setbeamertemplate{theorem begin}
+%   {\usebeamercolor[fg]{thcolor}% for the heading
+%   {\bfseries\inserttheoremname~}%
+%   \ifx\inserttheoremaddition\@empty\else(\inserttheoremaddition)\ \fi%
+%   \hspace{.01em}\normalfont\usebeamercolor[fg]{thcolor}% for the body
+%   }
+% \setbeamertemplate{theorem end}{}
+% \makeatother
 %----------------------------------------------------------------------------------------
@@
 When $p(\theta)$ is the posterior distribution of some parameters given a set of data $X_1,\ldots, X_n$, i.e.,
-\[
+$$
 p(\theta) = \prod_{i=1}^n P(X_i|\theta) P(\theta),
-\]
+$$
 The noisy gradient step in Algorithm 1 can be estimated by subsampling:
+
 (Central limit theorem)
@@
 \begin{block}{Upper Bound On Mixing Time}
-How effective Algorithm 1 is as a sampling method? Denote $\|\cdot\|_{\mathrm{TV}}$ the TV norm and $P^t(\bx^0)$ the density of $\bx^t$ starting from $\bx^0$. Define its mixing time to be
+How effective is Algorithm 1 as a sampling method? Denote $\|\cdot\|_{\mathrm{TV}}$ the TV norm and $P^t(\bx^0)$ the density of $\bx^t$ starting from $\bx^0$. Define its mixing time to be
 \[
@@
 \]
-Suppose $\tau_{\bx^0}$ is the stopping time when the algorithm converges to global minimum starting from $\bx^0$, we might be able to have a upper bound for $\tau_{\mathrm{mix}}$.
+Suppose $\tau_{\bx^0}$ is the stopping time when the algorithm converges to the global minimum starting from $\bx^0$, we might be able to have an upper bound for $\tau_{\mathrm{mix}}$.
 \[
@@
 \item Proved accurate stationary distribution based on oracle results
-\item Established connection between SGD and maximize \emph{a posteriori}
+\item Established connection between SGD and maximum \emph{a posteriori}
 \item Derived upper bound on mixing time

### 2016-12-07 paper/main.tex
Updates from ShareLaTeX

--- 2016-12-05 paper/main.tex
@@
 \begin{abstract}
-Stochastic gradient descent (SGD), under mild conditions, can be viewed as a Markov chain.
+Stochastic gradient descent (SGD), under mild conditions, can be viewed as a Markov chain sampler.
 This relationship has been pointed out in a variety of papers \cite{kushner2012stochastic, bach2014adaptivity}.
@@
 Specifically,  we would like to explore mixing time related issues and obtain some novel theoretical and empirical findings on the mixing time of SGD (If successful).
-A specific question to answer is whether lower mixing time will imply faster convergence rate.
-The hunch is that if the corresponding Markov chain has a low mixing time, SGD should converge fast.
+The hunch is that if SGD converges fast, it will have a low mixing time.
 This seems to be a novel perspective to understand SGD.
@@
 Theoretical analysis as well as empirical experiments will be carried out to further explore this issue.
+
+During the poster session, the proposed method seems to be a rediscovery of the Langevin MCMC sampling.
 
@@
 
-\begin{algorithm}
+Define $\D(\R^p)$ to be the family of the density functions of smooth random variables in $\R^p$, i.e.,
+
+\begin{equation}
+\D(\R^p)\triangleq \{p(\bx)\Big| p\in C^1(\R^p),~p(\bx) \geq 0,~ \int_\bx p(\bx) = 1.\}
+\end{equation}
+Suppose we would like to sample from a distribution $p(\bx)\in \D(\R^p) \propto f(\bx)$. 
+\begin{algorithm}[H]
 {\small
-Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$,
+Given $f(x)$, 
 \begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
 \STATE {\bf Initialize} $ \bx^0$ arbitrarily;
-\WHILE{stopping criterion not satisfied}
-\STATE draw $\epsilon^t$ from Gaussian distribution $\N(0, \sigma^2)$.
+\WHILE{burn-in period}
+\STATE draw $a^t$ from Gaussian distribution $\N(\nabla \log f(\bx^k), \Sigma^{t})$.
 \STATE
-$\bx^{k+1} \gets \bx^k - \alpha\nabla f(\bx^k) + \epsilon^t$;
+$\bx^{k+1} \gets \bx^k + (2\Sigma^t)^{-1} a^t$;
 \STATE $k\gets k+1$;
@@
 
-Define $\D(\R^p)$ to be the family of the density functions of smooth random variables in $\R^p$, i.e.,
-
-\begin{equation}
-\D(\R^p)\triangleq \{p(\bx)\Big| p\in C^1(\R^p),~p(\bx) \geq 0,~ \int_\bx p(\bx) = 1.\}
-\end{equation}
 Consider any $p(\bx)\in \D(\R^p)$, we have the following theorem:
@@
 
-Some empirical demonstration. How accurate is this approximation?
-
-Since this is only a very rough deduction, we would like to examine the stationary distribution of SGD empirically for some special cases.
+Note that this is only a rough deduction instead of an accurate proof.
+The problem of this deduction is two-fold.
+First, the equality only holds approximately.
+Second, SGD sampler's stationary distribution might not satisfy the detailed balance condition.
+Therefore, we would like to examine the stationary distribution of SGD empirically for some special cases.
 
@@
     \includegraphics[width=.3\textwidth]{../figure/case3_step_0.005_iter_1e5.png}
-    \caption{Experiment 1: the empirical histogram using SGD.
-Each column corresponds to a different number of samples ($1e3$, $1e4$, and $1e5$), each row corresponds to a different distrubtion ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$}
+    \caption{Empirical stationary distribution using SGD.
+Different columns correspond to different samples sizes ($1e3$, $1e4$, and $1e5$).
+Different rows correspond to different distributions ($f_1(x) = \exp(-x^4)$, $f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$, $f_3(x) = \exp(-|x|)$.}
     \label{Fig:exp1}
@@
 \begin{theorem}[Central limit theorem]
-Let $K = \alpha^{-1} \var \log P(X_1|\theta^t)$,
+Let $K$ be the subsampling size and $\eta_1,\ldots, \eta_K$ be samples drawing from $1,\ldots, n$ with replacement, then
 \[
-\sum_{i=1}^K (K^{-1}\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) - (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) \sim \N(0, \alpha).
+K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
 \]
 \end{theorem}
+
 \begin{algorithm}
@@
 
-A toy example showing SGD works.
+\begin{experiment}
+Consider the empirical/real density for $(\mu, \sigma^2)$ where $p(X_1|\mu, \sigma^2)\sim \N(\mu, \sigma^2)$, data $X_1,\ldots, X_{1000}$ is drawn from $\N(0, 1)$, $K = 1000$, sample size is $1000$.
+The empirical density is close to the real density.
+Note that variance $\sigma^2$ has higher variance than the expectation $\mu$
+\end{experiment}
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{../figure/simulation2_empirical.png}
+\includegraphics[width=0.5\linewidth]{../figure/simulation2_real.png}
+\caption{The empirical/real density for $(\mu, \sigma^2)$ where $p(X_1|\mu, \sigma^2)\sim \N(\mu, \sigma^2)$, data $X_1,\ldots, X_{1000}$ is drawn from $\N(0, 1)$, $K = 1000$, sample size is $1000$.
+The empirical density is close to the real density.
+Note that variance $\sigma^2$ has higher variance than the expectation $\mu$}
+\end{figure}
 % ===================================================================================
@@
 In the past literature, the upperbound of a mixing time can be obtained by a coupling technique.
-Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $d(t) = \max_{x\in \Omega} \|P^t(x, \cdot), \pi(\cdot)\|_{TV}$, and $\bar{d}(t) = \max_{x,y\in \Omega} \|P^t(x, \cdot), P^t(y,\cdot)\|_{TV}$.
-Define $t_{mix} = \min\{t:d(t) < \epsilon\}$.
-\begin{conjecture}[Upperbound for mixing time] $\tau$ is the convergence stoppiing time. $\tau_{mix} \leq 2 \max_{x} \E_{x}(\tau)$.
+Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $P^t(\bx^0)$ the density of $\bx^t$ starting from $\bx^0$, $d(t) = \max_{x\in \Omega} \|P^t(x, \cdot), \pi(\cdot)\|_{TV}$, and $\bar{d}(t) = \max_{x,y\in \Omega} \|P^t(x, \cdot), P^t(y,\cdot)\|_{TV}$.
+Define its mixing time to be 
+\[
+\tau_{\mathrm{mix}} \triangleq \min\{t|\max_{\bx^0}\|P^t(\bx^0) - p\|_{\mathrm{TV}}\leq 1/4\}.
+\]
+
+\begin{conjecture}[Upperbound for mixing time] Suppose $\tau_{\bx^0}$ is the stopping time when the algorithm converges to global minimum starting from $\bx^0$, we might be able to have a upper bound for $\tau_{\mathrm{mix}}$.
+\[
+\tau_{\mathrm{mix}} \leq 4 \max_{\bx^0}\E \tau_{\bx^0}.
+\]
 \end{conjecture}
+
+So the conjecture is that when SGD converges fast, it will also be efficient as a sampling method.
+
 % section upper_bound_on_the_mixing_time (end)
@@
 \label{sec:discussion}
+In this paper, we rediscovered Langevin SGD-based sampler and researched on its stationary distribution, mixing time, and how to use it to do posterior sampler. 
+\begin{enumerate}
+    \item When the objective of SGD is chosen to be $\log f(x)$, the stationary distribution is approximately the same as $f(x)$.
+Empirical simulation shows even if $f(\cdot)$ has two modes, SGD sampler will still reach a pretty accurate distribution.
+    \item When sampling from a posterior distribution, the SGD update step can be estimated using a randomly chosen subset of the whole dataset.
+A toy example of estimating the expectation and variance of a Gaussian distribution demonstrate its performance.
+    \item We also carried out a comparison between SGD's mixing time and its convergence time. Empirical simulations show that when SGD converges fast, it will also have a small mixing time.
+\end{enumerate}
+Future work includes:
+\begin{enumerate}
+    \item we will dig into the literature on Langevin MCMC and learn more about this issue. 
+    \item Current analysis cannot apply to the multiple-mode distribution.
+The simple simulation showed SGD, although very slow, still works in that case.
+Thus we might be able to consider this scenario in the future.
+    \item The mixing time of SGD based sampling will be prohibitively large when multiple modes are present. We would also like to consider how to overcome this issue.
+\end{enumerate}
 
-$f_1(x) = \exp(-x^4)$
+\section{Acknowledgement}
 
-$f_2(x) = \exp(-(x^2 - 4)(x^2 - 1))$
-
-$f_3(x) = \exp(-|x|)$
-
-- what we have achieved
-
-- Future work
+We would like to thank Professor Martin Wainwright for his inspiring teaching this semester.
+And we also greatly appreciate Arturo Fernandez and Jeffery Chan, our GSIs, for their devotion in this course.
 

### 2016-12-07 paper/main.tex

@@
 \label{sec:discussion}
-In this paper, we rediscovered Langevin SGD-based sampler and researched on its stationary distribution, mixing time, and how to use it to do posterior sampler. 
+
+In this paper, we have shown that stochastic gradient descent approaches extend in an elegant way to a sampler for posterior distributions when computing the likelihood from the full data is intensive.
+We are able to establish the stationary distribution of the procedure and gave several examples showing the accuracy and uses of our result.
+By taking a Bayesian route, we are able to show that the SGD algorithm is a sampler of a posterior under a non-informative prior.
+This enables us to establish connection between SGD and maximum \emph{a posteriori} (MAP) procedure, which is an analogy to gradient descent solving a maximum likelihood estimator in the frequentist paradigm.
+A natural extension of this work, which we hope to be able to accomplish, is to derive finite sample rates of convergence for the mixing time, which would allow a more rigor understanding of the SGD family as a whole.
+Extensive simulation of the methodology is also needed to fully understand this novel SGD sampler.
+
+A detailed contribution is summarized as the following:
 \begin{enumerate}

### 2016-12-07 code/final/1_1/mixing.py
correct ver

@@ -48,13 +48,23 @@ def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
 # graph(ecdf, range(-3, 3))
 # graph(station_cdf, range(-3, 3))
 def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
-    # ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    # all_traject = pickle.load(open('all_traject.pickle', 'rb'))
+    # emp_samples = all_traject[100,:]
+    # a= -3
+    # b=3
+    # dx=.01
+
     X  = np.arange(a,b,dx)
     kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
     e_pdf = kde.evaluate(X) # vector of pdf value
 
     station_pdf = pdf_normalize(pdf_func = station_func, a=a, b=b, dx=dx)
     t_pdf = station_pdf(X)
+
+    # plt.figure()
+    # plt.plot(X, e_pdf)
+    # plt.plot(X, t_pdf)
+    # plt.savefig('density.pdf', format='pdf')
 
     return np.mean(abs(e_pdf - t_pdf))
 
@@ -122,11 +132,14 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
     for it in range(0,N_total):
         l1_all[it] = pdf_l1(emp_samples = all_traject[it,:], station_func = station_func, a=a, b=b, dx=dx)
 
-    # plt.plot(l1_all)
-    # plt.savefig('yo.pdf', format='pdf')
 
     pickle.dump(obj = l1_all, file = open('./l1_all.pickle', 'wb'), protocol=pickle.HIGHEST_PROTOCOL)
-    # l1_all = pickle.load('l1_all.pickle')
+    # l1_all = pickle.load(open('l1_all.pickle', 'rb'))
+
+    # plt.figure()
+    # plt.plot(l1_all[0:400])
+    # plt.ylim((0, .5))
+    # plt.savefig('l1.pdf', format='pdf')
 
     is_mix = l1_all <= epsilon_norm
 

### 2016-12-07 code/final/1_2/mixing.py

@@ -48,13 +48,22 @@ def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
 # graph(ecdf, range(-3, 3))
 # graph(station_cdf, range(-3, 3))
 def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
-    # ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    # all_traject = pickle.load(open('all_traject.pickle', 'rb'))
+    # emp_samples = all_traject[100,:]
+
     X  = np.arange(a,b,dx)
     kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
     e_pdf = kde.evaluate(X) # vector of pdf value
 
     station_pdf = pdf_normalize(pdf_func = station_func, a=a, b=b, dx=dx)
     t_pdf = station_pdf(X)
+
+
+    # plt.figure()
+    # plt.plot(X, e_pdf)
+    # plt.plot(X, t_pdf)
+    # plt.savefig('density.pdf', format='pdf')
+
 
     return np.mean(abs(e_pdf - t_pdf))
 
@@ -122,11 +131,13 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
     for it in range(0,N_total):
         l1_all[it] = pdf_l1(emp_samples = all_traject[it,:], station_func = station_func, a=a, b=b, dx=dx)
 
-    # plt.plot(l1_all)
-    # plt.savefig('yo.pdf', format='pdf')
+    # plt.figure()
+    # plt.plot(l1_all[0:400])
+    # plt.ylim((0, .5))
+    # plt.savefig('l1.pdf', format='pdf')
 
     pickle.dump(obj = l1_all, file = open('./l1_all.pickle', 'wb'), protocol=pickle.HIGHEST_PROTOCOL)
-    # l1_all = pickle.load('l1_all.pickle')
+    # l1_all = pickle.load(open('l1_all.pickle', 'rb'))
 
     is_mix = l1_all <= epsilon_norm
 

### 2016-12-07 code/final/1_3/mixing.py

@@ -48,13 +48,22 @@ def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
 # graph(ecdf, range(-3, 3))
 # graph(station_cdf, range(-3, 3))
 def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
-    # ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    # all_traject = pickle.load(open('all_traject.pickle', 'rb'))
+    # emp_samples = all_traject[100,:]
+
+
     X  = np.arange(a,b,dx)
     kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
     e_pdf = kde.evaluate(X) # vector of pdf value
 
     station_pdf = pdf_normalize(pdf_func = station_func, a=a, b=b, dx=dx)
     t_pdf = station_pdf(X)
+
+    # plt.figure()
+    # plt.plot(X, e_pdf)
+    # plt.plot(X, t_pdf)
+    # plt.savefig('density.pdf', format='pdf')
+
 
     return np.mean(abs(e_pdf - t_pdf))
 
@@ -122,11 +131,13 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
     for it in range(0,N_total):
         l1_all[it] = pdf_l1(emp_samples = all_traject[it,:], station_func = station_func, a=a, b=b, dx=dx)
 
-    # plt.plot(l1_all)
-    # plt.savefig('yo.pdf', format='pdf')
+    # plt.figure()
+    # plt.plot(l1_all[0:400])
+    # plt.ylim((0, .5))
+    # plt.savefig('l1.pdf', format='pdf')
 
     pickle.dump(obj = l1_all, file = open('./l1_all.pickle', 'wb'), protocol=pickle.HIGHEST_PROTOCOL)
-    # l1_all = pickle.load('l1_all.pickle')
+    # l1_all = pickle.load(open('l1_all.pickle', 'rb'))
 
     is_mix = l1_all <= epsilon_norm
 

### 2016-12-07 code/final/1_4/mixing.py

@@ -48,13 +48,23 @@ def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
 # graph(ecdf, range(-3, 3))
 # graph(station_cdf, range(-3, 3))
 def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
-    # ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    # all_traject = pickle.load(open('all_traject.pickle', 'rb'))
+    # emp_samples = all_traject[400,:]
+    # a= -3
+    # b=3
+    # dx=.01
+
     X  = np.arange(a,b,dx)
     kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
     e_pdf = kde.evaluate(X) # vector of pdf value
 
     station_pdf = pdf_normalize(pdf_func = station_func, a=a, b=b, dx=dx)
     t_pdf = station_pdf(X)
+
+    # plt.figure()
+    # plt.plot(X, e_pdf)
+    # plt.plot(X, t_pdf)
+    # plt.savefig('density.pdf', format='pdf')
 
     return np.mean(abs(e_pdf - t_pdf))
 
@@ -122,11 +132,15 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
     for it in range(0,N_total):
         l1_all[it] = pdf_l1(emp_samples = all_traject[it,:], station_func = station_func, a=a, b=b, dx=dx)
 
-    # plt.plot(l1_all)
-    # plt.savefig('yo.pdf', format='pdf')
 
     pickle.dump(obj = l1_all, file = open('./l1_all.pickle', 'wb'), protocol=pickle.HIGHEST_PROTOCOL)
     # l1_all = pickle.load(open('l1_all.pickle', 'rb'))
+
+    # plt.figure()
+    # plt.plot(l1_all[0:400])
+    # plt.ylim((0, .5))
+    # plt.savefig('l1.pdf', format='pdf')
+
 
     is_mix = l1_all <= epsilon_norm
 

### 2016-12-07 code/final/2_2/mixing.py

@@ -44,17 +44,21 @@ def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
 #     val2 = cdf2(X)
 #     return np.mean(abs(val1 - val2))
 # ====================================================================================
-# plt.figure()
-# graph(ecdf, range(-3, 3))
-# graph(station_cdf, range(-3, 3))
 def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
-    # ecdf = sm.distributions.empirical_distribution.ECDF(emp_samples)
+    # all_traject = pickle.load(open('all_traject.pickle', 'rb'))
+    # emp_samples = all_traject[100,:]
+
     X  = np.arange(a,b,dx)
     kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
     e_pdf = kde.evaluate(X) # vector of pdf value
 
     station_pdf = pdf_normalize(pdf_func = station_func, a=a, b=b, dx=dx)
     t_pdf = station_pdf(X)
+
+    # plt.figure()
+    # plt.plot(X, e_pdf)
+    # plt.plot(X, t_pdf)
+    # plt.savefig('density.pdf', format='pdf')
 
     return np.mean(abs(e_pdf - t_pdf))
 
@@ -122,11 +126,13 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
     for it in range(0,N_total):
         l1_all[it] = pdf_l1(emp_samples = all_traject[it,:], station_func = station_func, a=a, b=b, dx=dx)
 
-    # plt.plot(l1_all)
-    # plt.savefig('yo.pdf', format='pdf')
+    # plt.figure()
+    # plt.plot(l1_all[0:9000])
+    # plt.ylim((0, .5))
+    # plt.savefig('l1.pdf', format='pdf')
 
     pickle.dump(obj = l1_all, file = open('./l1_all.pickle', 'wb'), protocol=pickle.HIGHEST_PROTOCOL)
-    # l1_all = pickle.load('l1_all.pickle')
+    # l1_all = pickle.load(open('l1_all.pickle', 'rb'))
 
     is_mix = l1_all <= epsilon_norm
 

### 2016-12-07 code/final/2_2/proof_of_concept.py

@@ -73,7 +73,7 @@ def ProofOfConcept():
     def grad(x):
         return -degree * np.power(x, degree - 1)
     trajectory, image, haltIter = GD(func, grad, initialPoint=1., stepsize=1e-2/2,
-                                     noiseLevel=1e-1, maxIter=int(1e7), desiredObj=100)
+                                     noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
     #plt.figure()
     #plt.plot(trajectory[0:haltIter], image[0:haltIter])
     plt.figure()
@@ -99,8 +99,8 @@ def ProofOfConcept2():
     def grad(x):
         return (-4 * x ** 3 + 10 * x) * c
     trajectory, image, haltIter = GD(func, grad, initialPoint=1., stepsize=1e-2/2,
-                                     noiseLevel=1e-1, maxIter=int(1e7), desiredObj=100)
-                                     # noiseLevel=1e-1, maxIter=int(1e4), desiredObj=100)
+                                     noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
+                                     # noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)
     #plt.figure()
     #plt.plot(trajectory[0:haltIter], image[0:haltIter])
     plt.figure()
@@ -128,7 +128,7 @@ def GD_UnitTest(order = 1):
     def grad(x):
         return order * np.power(abs(x), order - 1)
     trajectory, image, haltIter = GD(func, grad, initialPoint=1e-3, stepsize=1e-4/2,
-                                     noiseLevel=1e-2, maxIter=int(1e6), desiredObj=1)
+                                     noiseLevel=1e-2, maxIter=int(1e5), desiredObj=1)
     # the
     plt.figure()
     plt.plot(trajectory[0:haltIter], image[0:haltIter])

### 2016-12-07 code/final/2_2/simulation.py

@@ -5,7 +5,7 @@ import scipy as sp
 import statsmodels as sm
 import ipyparallel
 
-def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e4), desiredObj = 100, verbose = False):
+def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, verbose = False):
     trajectory_all = []
     image_all = []
     haltIter_all = []
@@ -21,7 +21,7 @@ def simu_all(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-
 
 # $ ipcluster start -n 3
 # $ ipcluster start -n 24
-def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e4), desiredObj = 100, burn_in = 1e3):
+def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter = int(1e5), desiredObj = 100, burn_in = 1e3):
     clients = ipyparallel.Client()
     dview = clients.direct_view()
 
@@ -63,4 +63,4 @@ def simu_all_parallel(n_sim, func, grad, initialPoint=1., stepsize=1e-2/2, noise
 
     return all_traject
 
-# %time all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e4), desiredObj=100)
+# %time all_traject = simu_all_parallel(n_sim = 1e2, func = func, grad = grad, initialPoint=1., stepsize=1e-2/2, noiseLevel=1e-1, maxIter=int(1e5), desiredObj=100)

### 2016-12-07 code/final/2_2/mixing.py
final figure

@@ -45,20 +45,23 @@ def pdf_normalize(pdf_func, a = -3, b = 3, dx = .01):
 #     return np.mean(abs(val1 - val2))
 # ====================================================================================
 def pdf_l1(emp_samples, station_func, a= -3, b=3, dx=.01):
-    # all_traject = pickle.load(open('all_traject.pickle', 'rb'))
-    # emp_samples = all_traject[100,:]
+    all_traject = pickle.load(open('all_traject.pickle', 'rb'))
+    emp_samples = all_traject[99998,:]
+    # emp_samples = all_traject[200,:]
+    emp_samples = all_traject[9999,:]
 
     X  = np.arange(a,b,dx)
-    kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
+    # kde = sp.stats.gaussian_kde(emp_samples, bw_method=None)
+    kde = sp.stats.gaussian_kde(emp_samples, bw_method=0.02)
     e_pdf = kde.evaluate(X) # vector of pdf value
 
     station_pdf = pdf_normalize(pdf_func = station_func, a=a, b=b, dx=dx)
     t_pdf = station_pdf(X)
 
-    # plt.figure()
-    # plt.plot(X, e_pdf)
-    # plt.plot(X, t_pdf)
-    # plt.savefig('density.pdf', format='pdf')
+    plt.figure()
+    plt.plot(X, e_pdf)
+    plt.plot(X, t_pdf)
+    plt.savefig('density.pdf', format='pdf')
 
     return np.mean(abs(e_pdf - t_pdf))
 
@@ -127,7 +130,8 @@ def mixing_time(all_traject, station_func, epsilon_norm = 1/4, a=-3, b=3, dx=.01
         l1_all[it] = pdf_l1(emp_samples = all_traject[it,:], station_func = station_func, a=a, b=b, dx=dx)
 
     # plt.figure()
-    # plt.plot(l1_all[0:9000])
+    # plt.plot(l1_all[0:9999])
+    # # plt.plot(l1_all[0:500])
     # plt.ylim((0, .5))
     # plt.savefig('l1.pdf', format='pdf')
 

### 2016-12-07 paper/main.tex
Updates from ShareLaTeX

@@
 \WHILE{burn-in period}
-\STATE draw $a^t$ from Gaussian distribution $\N(\nabla \log f(\bx^k), \Sigma^{t})$.
+\STATE draw $a^k$ from Gaussian distribution $\N(\nabla \log f(\bx^k), \Sigma^{k})$.
 \STATE
-$\bx^{k+1} \gets \bx^k + (2\Sigma^t)^{-1} a^t$;
+$\bx^{k+1} \gets \bx^k + (2\Sigma^k)^{-1} a^k$;
 \STATE $k\gets k+1$;
@@
 
-Consider any $p(\bx)\in \D(\R^p)$, we have the following theorem:
+Consider any $p(\bx)\in \D(\R^p)$, we have the following conjecture:
 
 \begin{conjecture}
-For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, 2\epsilon)$.
+For any $p(\bx)\in \D(\R^p)$, it is approximately the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, 2\epsilon)$.
 \end{conjecture}
@@
 Let's verify this theorem by checking the detailed balance condition.
-Denote $g(\by|\bx)$ to be the density function of the transition, because $\by = \bx - \alpha \nabla f(\bx^k) + \epsilon^t$ and $\epsilon^t\sim \N(0, \sigma^2)$, we know
+Denote $g(\by|\bx)$ to be the density function of the transition, because $\by = \bx - \alpha \nabla f(\bx^k) + \epsilon^k$ and $\epsilon^k\sim \N(0, \sigma^2)$, we know
 \begin{equation}
@@
 \[
-\theta^{t+1} \gets \theta^{t} + \alpha (n^{-1} \sum_i \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) + \epsilon^t.
+\theta^{k+1} \gets \theta^{k} + \alpha (n^{-1} \sum_i \nabla \log P(X_i|\theta^k) - \log P(\theta^k)) + \epsilon^k.
 \]
-Note that $\alpha (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) + \epsilon^t$ can be approximated by
+Note that $\alpha (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^k) - \log P(\theta^k)) + \epsilon^k$ can be approximated by
 \[
-\sum_{i=1}^K (K^{-1} \nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)),
+\sum_{i=1}^K (K^{-1} \nabla \log P(X_{\eta_i}|\theta^k) - \log P(\theta^k)),
 \]
@@
 \[
-K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
+K^{-1}\sum_{i=1}^K (\nabla \log P(X_{\eta_i}|\theta^k) - \log P(\theta^k)) \sim \N(n^{-1} \nabla \log p(\theta) , K^{-1}\cov \nabla \log p(\theta)).
 \]
@@
 \STATE draw $K$ iid samples with replacement from $1,\ldots, n$, denoted $\eta_1,\ldots, \eta_K$.
-\STATE calculate the mean $a^t$ and the covariance matrix $\Sigma^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
+\STATE calculate the mean $a^k$ and the covariance matrix $\Sigma^k$ of $(\nabla\log p(X_{\eta_i}|\theta^k))_{i=1}^K$.
 \STATE
-$\theta^{t+1} \gets \theta^t + 2(\Sigma^t)^{-1}a^t$;
-\STATE $t\gets t+1$;
+$\theta^{k+1} \gets \theta^k + 2(\Sigma^k)^{-1}a^k$;
+\STATE $k\gets k+1$;
 \ENDWHILE
@@
 In the past literature, the upperbound of a mixing time can be obtained by a coupling technique.
-Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $P^t(\bx^0)$ the density of $\bx^t$ starting from $\bx^0$, $d(t) = \max_{x\in \Omega} \|P^t(x, \cdot), \pi(\cdot)\|_{TV}$, and $\bar{d}(t) = \max_{x,y\in \Omega} \|P^t(x, \cdot), P^t(y,\cdot)\|_{TV}$.
+Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $P^k(\bx^0)$ the density of $\bx^k$ starting from $\bx^0$, $d(k) = \max_{x\in \Omega} \|P^k(x, \cdot), \pi(\cdot)\|_{TV}$, and $\bar{d}(k) = \max_{x,y\in \Omega} \|P^k(x, \cdot), P^k(y,\cdot)\|_{TV}$.
 Define its mixing time to be 
 \[
-\tau_{\mathrm{mix}} \triangleq \min\{t|\max_{\bx^0}\|P^t(\bx^0) - p\|_{\mathrm{TV}}\leq 1/4\}.
+\tau_{\mathrm{mix}} \triangleq \min\{k|\max_{\bx^0}\|P^k(\bx^0) - p\|_{\mathrm{TV}}\leq 1/4\}.
 \]
@@
 So the conjecture is that when SGD converges fast, it will also be efficient as a sampling method.
+
+In order to explore this issue empirically, we designed the following experiment.
+\begin{experiment}
+Calculate $d(k)$, namely the TV distance between empirical pdf (using Gaussian kernel) and expected pdf for the following 5 density functions:
+\begin{enumerate}
+    \item $P(x) \propto \exp(- |x|)$
+    \item $P(x) \propto \exp(- |x|^2)$
+    \item $P(x) \propto \exp(- |x|^3)$
+    \item $P(x) \propto \exp(- |x|^4)$
+    \item $P(x) \propto \exp(- (x^ - 4)(x^2 - 1))$
+\end{enumerate} 
+\end{experiment}
+\begin{figure}
+\centering
+
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}\\
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
+\caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
+It can be seen that $d(k)$ decreases exponentially for all of the functions.
+And the mixing time decreases as the degree increases.}\label{Fig:sim3_1}
+\end{figure}
+\begin{figure}
+\centering
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}\\
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
+\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
+For $\exp(-|x|)$, it has not converge to the true pdf yet.
+For $\exp(-|x|^4)$, it has already converged.}\label{Fig:sim3_2}
+\end{figure}
+As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest (> 100) and the mixing time of $\exp(-|x|^4)$ is the shortest.
+This is coherent with their convergence time.
+For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.
+\begin{figure}
+\centering
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
+\caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
+\caption{$d(k)$, difference between the empirical pdf and the expected pdf for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_4}
+\end{figure}
+As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^4= 1))$ is much longer than any single mode distribution.
+Its convergence time is also the longest.
 

### 2016-12-07 paper/main.tex
minor clean

@@
 \end{figure}
-As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest (> 100) and the mixing time of $\exp(-|x|^4)$ is the shortest.
+As shown in Figure \ref{Fig:sim3_1} and Figure \ref{Fig:sim3_2}, the mixing time of $\exp(-|x|)$ is the longest ($>$ 100) and the mixing time of $\exp(-|x|^4)$ is the shortest.
 This is coherent with their convergence time.
 For $\exp(-|x|)$, the convergence time is the longest; for $\exp(-|x|^4)$, the convergence time is the longest.
+
+\begin{table}[h!]
+\centering
+\begin{tabular}{ll}
+\hline
+Density & Median convergence time \\
+\hline
+1        & 164\\
+2        & 144\\
+3        & 138\\
+4        & 129\\
+5        & 21480\\
+\hline
+\end{tabular}
+\caption{Median convergence time of the five target densities}
+\label{tbl:med_conv_time}
+\end{table}
+
 \begin{figure}
 \centering
-\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
+% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
+% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
+% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
 \caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
@@
 \centering
-\includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
+% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
 \caption{$d(k)$, difference between the empirical pdf and the expected pdf for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_4}
 \end{figure}
-As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^4= 1))$ is much longer than any single mode distribution.
+As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^4 - 1))$ is much longer than any single mode distribution.
 Its convergence time is also the longest.
@@
 % section upper_bound_on_the_mixing_time (end)
-
+\newpage
 % ===================================================================================
@@
 % section discussion (end)
-\newpage
+% \newpage
 % ===================================================================================
@@
 %% appendix sections are then done as normal sections
-\appendix
+% \appendix
 
-\section{Section in Appendix}
-\label{appendix-sec1}
+% \section{Section in Appendix}
+% \label{appendix-sec1}
 
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text.
+% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
+% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
+% Sample text.
 

### 2016-12-07 paper/main.tex
Updates from ShareLaTeX

--- 2016-12-07 paper/main.tex
@@
 \usepackage{grffile}
-
+\usepackage{listings}
 %% The lineno packages adds line numbers. Start line numbering with
@@
 Take the density function of $X$ to be $f(x) \propto \exp(- x^4)$, let $2\sigma^2 = \epsilon = 0.005$, $x_0 = 1$, burning-in period is $1000$, waiting period is $1000$, the empirical histogram v.s.
-the desired histogram is plotted in Figure ???
+the desired histogram is plotted in Figure 1.
 \end{experiment}
@@
 \includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}\\
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_l1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case2_l1.pdf}\\
+\includegraphics[width=.3\textwidth]{../figure/sim3/case3_l1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case4_l1.pdf}
 \caption{$d(k)$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
@@
 \includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}\\
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case2_pdf.pdf}\\
+\includegraphics[width=.3\textwidth]{../figure/sim3/case3_pdf.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case4_pdf.pdf}
 \caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
@@
 \appendix
-
-\section{Section in Appendix}
-\label{appendix-sec1}
-
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-Sample text.
+\tiny
+\lstinputlisting[language=python]{../code/final/1_1/convergence.py}
+\lstinputlisting[language=python]{../code/final/1_1/example1_1.ipy}
+\lstinputlisting[language=python]{../code/final/1_1/simulation.py}
+\lstinputlisting[language=python]{../code/final/1_1/mixing.py}
+\lstinputlisting[language=python]{../code/final/1_1/proof_of_concept.py}
 

### 2016-12-07 paper/main.tex
Updates from ShareLaTeX

@@
 \includegraphics[width=.3\textwidth]{../figure/sim3/case4_pdf.pdf}
-\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
+\caption{Empirical density of $x^k$ for $k = 200$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
 For $\exp(-|x|)$, it has not converge to the true pdf yet.

### 2016-12-07 paper/main.tex

--- 2016-12-07 paper/main.tex
@@
 \includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}\\
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
-\includegraphics[width=.3\textwidth]{../figure/sim3/case1_pdf.pdf}
-\caption{Empirical density of $x^k$ for $k = 100$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
+\includegraphics[width=.3\textwidth]{../figure/sim3/case2_pdf.pdf}\\
+\includegraphics[width=.3\textwidth]{../figure/sim3/case3_pdf.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case4_pdf.pdf}
+\caption{Empirical density of $x^k$ for $k = 200$ for $\exp(- |x|)$ (upper left), $\exp(- |x|^2)$ (upper right), $\exp(- |x|^3)$ (lower left), $\exp(- |x|^4)$ (lower right).
 For $\exp(-|x|)$, it has not converge to the true pdf yet.
@@
 %% appendix sections are then done as normal sections
-% \appendix
-
-% \section{Section in Appendix}
-% \label{appendix-sec1}
-
-% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-% Sample text. Sample text. Sample text. Sample text. Sample text. Sample text.
-% Sample text.
+\appendix
+\tiny
+\lstinputlisting[language=python]{../code/final/1_1/convergence.py}
+\lstinputlisting[language=python]{../code/final/1_1/example1_1.ipy}
+\lstinputlisting[language=python]{../code/final/1_1/simulation.py}
+\lstinputlisting[language=python]{../code/final/1_1/mixing.py}
+\lstinputlisting[language=python]{../code/final/1_1/proof_of_concept.py}
 

### 2016-12-07 paper/main.tex
hahahahahahaha

@@
 \end{figure}
+\newpage
 % ===================================================================================
@@
 In the past literature, the upperbound of a mixing time can be obtained by a coupling technique.
-Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $P^k(\bx^0)$ the density of $\bx^k$ starting from $\bx^0$, $d(k) = \max_{x\in \Omega} \|P^k(x, \cdot), \pi(\cdot)\|_{TV}$, and $\bar{d}(k) = \max_{x,y\in \Omega} \|P^k(x, \cdot), P^k(y,\cdot)\|_{TV}$.
+Define $\|\cdot\|_{TV}$ to be the total variation norm of $\cdot$, $P^k(\bx^0)$ the density of $\bx^k$ starting from $\bx^0$, $d(k) = \max_{x\in \Omega} \|P^k(x, \cdot) - \pi(\cdot)\|_{TV}$, and $\bar{d}(k) = \max_{x,y\in \Omega} \|P^k(x, \cdot) - P^k(y,\cdot)\|_{TV}$.
 Define its mixing time to be
@@
     \item $P(x) \propto \exp(- |x|^4)$
-    \item $P(x) \propto \exp(- (x^ - 4)(x^2 - 1))$
+    \item $P(x) \propto \exp(- (x - 4)(x^2 - 1))$
 \end{enumerate}
@@
 \centering
-% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
-% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
-% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf2.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_pdf3.pdf}
 \caption{Empirical density of $x^k$ for $k = 100, 1000, 10000$ for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_3}
@@
 \centering
-% \includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
+\includegraphics[width=.3\textwidth]{../figure/sim3/case5_l1.pdf}
 \caption{$d(k)$, difference between the empirical pdf and the expected pdf for $\exp(- (x^2 - 1)(x^2 - 4))$. }\label{Fig:sim3_4}
 \end{figure}
-As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^4 - 1))$ is much longer than any single mode distribution.
+As shown in Figure \ref{Fig:sim3_3} and Figure \ref{Fig:sim3_4}, the mixing time of $\exp(-(x^2 - 1)(x^2 - 4))$ is much longer than any single mode distribution.
 Its convergence time is also the longest.
@@
 This enables us to establish connection between SGD and maximum \emph{a posteriori} (MAP) procedure, which is an analogy to gradient descent solving a maximum likelihood estimator in the frequentist paradigm.
-A natural extension of this work, which we hope to be able to accomplish, is to derive finite sample rates of convergence for the mixing time, which would allow a more rigor understanding of the SGD family as a whole.
-Extensive simulation of the methodology is also needed to fully understand this novel SGD sampler.
 
@@
 \end{enumerate}
+
 Future work includes:
